### 2023-01-04 augraphy_paper.tex
add new paper assets

% Created 2023-01-04 Wed 14:12
% Intended LaTeX compiler: pdflatex
\documentclass[runningheads]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsmath, amsthm, amsfonts, enumerate}
\author{Alexander Groleau, Samay Maini, Jonathan Boarman}
\date{\today}
\title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
\hypersetup{
 pdfauthor={Alexander Groleau, Samay Maini, Jonathan Boarman},
 pdftitle={Augraphy: An Augmentation Pipeline API for Modern Document Images},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Abstract}
\label{sec:orgb8a4f58}
We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks. A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy. The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.

\section{Introduction and Motivation}
\label{sec:org1b677d2}
Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\

Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths. However, collecting or otherwise determining a set of labels for training data is quite challenging.  In the case of text documents, most real-world dirty documents \emph{can't} come with clean ground-truths.\\

Most often, source documents are too old, and often were created before the advent of digital storage media. Some documents are one-offs, produced ad-hoc in the typewriter era, but many more still were printed directly from the text editor used to write them, with no copy saved even after it became possible to do so. Document analysis and understanding tasks require these clean images for analysis. For these reasons, it's much easier to take clean documents and add distorting features to them with a tool like Augraphy than to start with the warped images and find or create ground-truths.

\section{NoisyOffice}
\label{sec:orga476358}
Few datasets exist for out-of-the-box use in training document-specific models. Many other datasets containing modern documents exist, but are designed for tasks like layout detection [RDCL2019 cit], content extraction [Tobacco 800 cit], or handwriting recognition [ICDAR2019-CROHME-TDF cit]. In our investigations, the only publically available dataset we could find that was exclusively focused on digitally-generated documents was the NoisyOffice set [CASTRO-BLEDA].\\

The NoisyOffice dataset [paper link] was created as for document manipulation and analysis model training and validation. NoisyOffice includes three types of image:
\begin{enumerate}
\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
\end{enumerate}

While assembling the NoisyOffice database was a great service in its own right — no other such set seems to have been published — the NoisyOffice set is very limited:\\

\begin{itemize}
\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
\item the text is all English-language
\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models
\end{itemize}

Rather than providing a direct answer to these, Augraphy does not (yet) generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis taskwhile relying on users to supply the ground truth images.

\section{DocCreator}
\label{sec:orgf17073e}
In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator seeming to occupy that niche.\\

DocCreator contains character-set-level distortions, a mechanism for overlaying characters onto an arbitrary paper texture akin to merge technique \#1, and also includes an experimental tool for fusing the document image onto one of several 3D meshes to simulate physical alterations to the document like a crumpled and smoothed page.\\

While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \emph{modern} documents. Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in C++, making it unsuitable for use either in a data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration. More frustrating still, the software is buggy and crashes often, making even successfully generating a single augmented document image quite an ordeal.\\

Augraphy was not designed with historical documents in mind, but neither did its design preclude that possibility. Instead, the focus is on modern documents generated at least in part digitally.

\section{Document Distortion, Theory \& Technique}
\label{sec:org24682f8}
Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\

These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents. A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\

Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed has either a direct implementation already within the library or on the development roadmap, with more planned.\\

Some techniques exist for introducing these features into images of documents, including but not limited to the following:\\
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used. The NoisyOffice team did this.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
\end{enumerate}

Augraphy already has a story for the first three, with the fourth in planning.

\section{Augraphy}
\label{sec:org4a1c65c}
We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

The library contains 18 unique transformations — augmentations, in Augraphy's parlance — which may be sequenced into a pipeline object which carries out the image manipulation. Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.\\

Augraphy attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post. The ink phase exists to sequence effects which specifically alter the printed ink — like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time — and transform them prior to "printing". The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here we find the PaperFactory generator for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining. After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document. After "printing", the document enters the post-phase, wherein it may undergo alterations that would affect an already-printed document out in the world. Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on. A brief description of each augmentation appears in a table in the next section.

\section{The Augraphy API}
\label{sec:orgd64a7b1}
The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy. When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented datasets.\\

Modern frameworks for machine learning like \texttt{fastai} [Fastai: A Layered API for Deep Learning cit] aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility. We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults. The default Augraphy pipeline makes use of all of the augmentations available in Augraphy, with starting parameters selected after manual visual inspection of several thousand images. Adding a diverse array of realistic features to documents can be done with the following five-line incantation:

\begin{verbatim}
from augraphy import *
pipeline = default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented_img = data["output"]
\end{verbatim}

\subsection{Base}
\label{sec:org1182db0}
\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

There are four "main sequence" classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality. Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.

\subsubsection{Augmentation}
\label{sec:org73d5fe0}
Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1]. Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.\\

This class also contains a method which interacts with the probability data, dynamically generating a second floating point probability value and using this to decide whether the augmentation should be applied at runtime.

\subsubsection{AugmentationResult}
\label{sec:org6aeadfa}
After an augmentation is applied, the output of its execution is stored in an AugmentationResult object and passed forward through the pipeline. These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.

\subsubsection{AugmentationSequence}
\label{sec:org0192f11}
A list of Augmentations -- together with the intent to apply those Augmentations in sequence -- determines an AugmentationSequence, which is itself both an Augmentation and callable. In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of Augmentation constructor calls which produce callable Augmentation objects of the various flavors explored in \hyperref[sec:orgea493da]{Augmentations}. AugmentationSequences are applied to the image during each of the \hyperref[sec:org6690404]{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

\subsubsection{AugmentationPipeline}
\label{sec:org6690404}
The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life. Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples. Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository. An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.\\

Realistically reproducing effects in document images requires rethinking how those effects are produced in the real world. Many issues, like the various forms of misprint, only affect text and images on the page. Others, like a coffee spill, change properties of the paper itself. Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.\\

Effectively capturing processes like these in reproducible augmentations meant separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through. Augraphy pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases. After transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper. Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.\\

Use of the Augraphy library to produce a dataset for model training — will be covered in some detail later — boils down to the definition and application of one or more pipelines to one or more images.\\

The value added by the AugrapyPipeline class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an AugraphyPipeline application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation. This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.

\subsubsection{OneOf}
\label{sec:orgb9ecb78}
Real-world processes generally allow for objects to exist in multiple states over time. To model the possibility that a document image has undergone one and only one of a collection of Augmentations, we use OneOf, which simply selects one of those Augmentations from a given list, and uses this to modify the image.

\subsubsection{PaperFactory}
\label{sec:org16fabe6}
We often print on multiple sizes and kinds of paper, and out in the world we certainly \emph{encounter} such diverse documents. We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline. This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image. The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the "printing" onto another "sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database. Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

\subsection{Augmentations}
\label{sec:orgea493da}
The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}. We have already included many such transforms in the standard library, and have also provided \hyperref[sec:org8b47a22]{tools} for easily building new augmentations and integrating them into the Augraphy workflow.\\

Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset. Augmentations come in many flavors and types, varying not only in their visual effect but also in their software design. Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well. The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\

Table 1 contains a list of augmentations and a description of their simulated effects.

\begin{center}
\begin{tabular}{ll}
Augmentation & Effect\\
\hline
BadPhotoCopy & Regions of noise and shadow like those produced by a dirty photocopier.\\
BindingsAndFasteners & Staples, paper clips, punched holes, and other results of physical tools applied to a document.\\
BleedThrough & Ink bleeding through the page from the reverse side.\\
BookBinding & The page curling away from the scanner bed, towards the binding of a book or magazine.\\
Brightness & Adjusts the brightness of the whole image by a chosen multiplier.\\
BrightnessTexturize & Random noise in the brightnes channel of the image, which emulates various paper textures.\\
DirtyDrum & Deposits of dirt and ink-grime from dirty printer drums.\\
DirtyRollers & Dirty document scanners can leave roller lines on the page.\\
Dithering & Ordered or Floyd-Steinberg dithering is applied to simulate downsampling during document processing.\\
DustyInk & Random noise in the ink emulates dusty or inconsistent ink tone when combined with a blur.\\
Faxify & Faxing documents introduces artifacts related to errors in transmission.\\
Folding & Folded paper exhibits a visible warp effect around the folding axis\\
Gamma & Gamma controls several features, particularly relative brightness and contrast\\
Geometric & Basic spatial transformations like resizing, flipping, and rotation\\
Inkbleed & Creates a fuzzy edge emulating over-application of ink during printing.\\
Jpeg & JPEG compression artifacts (deep fry your documents!)\\
Letterpress & Regions of ink pressed unevenly onto paper by a printing press\\
LightingGradient & Introduces a shading pattern over the document, like a photograph with a partially-occluded light source\\
LowInkBlobs & When a printer's ink supply is low, some areas of prints receive less ink in spots than they should.\\
LowInkPeriodicLines & A set of parallel lines that repeat in a periodic fashion throughout the image.\\
LowInkRandomLines & A set of parallel lines randomly distributed throughout the image.\\
Markup & Adds strikethrough, highlighting, or underline effects to the text.\\
NoiseTexturize & Another method of emulating different paper textures, by introducing Gaussian noise into the paper layer.\\
PageBorder & Simulates the edges of background pages on one side of the foreground page.\\
PencilScribbles & Random pencil marks, like the product of an idle student.\\
SubtleNoise & Using a document scanner to digitize a page introduces imperfections in solid regions due to subtle lighting differences.\\
\end{tabular}
\end{center}

\subsection{Utilities}
\label{sec:org8b47a22}
Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience during use in unforseen contexts, such as with other libraries.

\begin{center}
\begin{tabular}{ll}
Class & Purpose\\
\hline
ComposePipelines & Provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.\\
FigshareDownloader & Functions to query and download files from Figshare, a popular online repository of research data.\\
Foreign & Provides a means of wrapping augmentations from other projects, like Albumentations and imgaug.\\
Function & Wraps an arbitrary Python function or a list of such functions into an augmentation.\\
ImageOverlay & Places a given foreground image onto a given background, either randomly or at a specified location.\\
NoiseGenerator & Generates noise masks for placement on other images or in implementations of other augmentations.\\
OverlayBuilder & Creates an image mask containing other images, like hole punches or binder clips, for overlay onto a document.\\
\end{tabular}
\end{center}

\section{Deep Learning with Augraphy}
\label{sec:org4d4729d}
Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks. This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data. The NoisyOffice team set a baseline for others to follow in ["The NoisyOffice Database: A corpus to train supervised machine learning filters for image processing" CASTRO-BLEDA]. We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate set for Augraphy analysis.\\

Models were trained on an NVidia A100 GPU on Google Colaboratory. All preprocessing, training, and testing was done from a Jupyter notebook, published on GitHub.

\subsection{Model Architecture}
\label{sec:org83264cc}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library. This network achieved a high score on the NoisyOffice Kaggle competition [citation for Michal Brezák's notebook on Kaggle \url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}]; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes. For more exploration of models trained to solve this competition's challenge, see Colin Priest's work here: [citation for Colin Priest \url{https://colinpriest.com/2015/11/15/an-even-dozen-denoising-dirty-documents-part-12/}].\\

This low-layer model contains two layers of a convolution, each followed by a ReLU activation function, then a batch normalization layer as the encoding step. After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively. The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is "unpacking" higher-dimensional features from its low-dimensional latent representation. After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier. Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions. This final convolution uses the sigmoid function as its activation function. All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

\subsection{Data Generation}
\label{sec:orgd8c063f}
Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\

The NoisyOffice data provided by Kaggle contains 144 ground truth images, 144 training images, and 72 validation images. For the Augraphy model, we produced a dataset 10x larger, by duplicating each of the ground truth images, then running 10 Augraphy pipelines against each copy. Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.\\

The NoisyOffice dataset contains folded sheets, wrinkled sheets, coffee stains, and footprint noise. The features given by the wrinkle and fold distortions can be mimicked with some Gaussian noise applied at various points along a line, and the features created by the stains and footprints can be mimicked with dark regions and thin lines. With Augraphy, we expected that we could use the BadPhotoCopy augmentation and the strikethrough behavior from the Markup augmentation to add these features to the ground-truth data, so we executed the following pipeline:

\begin{verbatim}
ink_phase = []
paper_phase = []
post_phase = [BadPhotoCopy(), Markup()]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{verbatim}

Generating these 1440 images took 35 seconds with the rendering job spread across the 64 cores of an AWS c7g.16xlarge instance.

\subsection{Training Regime}
\label{sec:org4144ef4}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

Training proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs. The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.\\

Both models were trained with mean squared error as the loss function, using the Adam optimizer.\\

The NoisyOffice model finished training with an average loss of 0.0010, a mean average error of 0.0150, validation loss of 7.4609e-04, validation mean average error of 0.0122. Training took an average of 190ms/step and 1s/epoch.\\

The Augraphy model finished training with an average loss of 0.0014, a mean average error of 0.0142, validation loss of 8.9985e-04, and validation mean average error of 0.0112. Training took roughly 218ms/step and 11s/epoch.

\subsection{Results}
\label{sec:org9fa72d2}
Sample predictions from each model on the validation task are presented in Figure 1. As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue. The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features. Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.\\

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./images/sidebyside.png}
\caption{\label{fig:org74839c0}Comparison of the validation image (left) and the images predicted by the NoisyOffice model (center) and Augraphy model (right)}
\end{figure}

To compare the models' performance on the validation task, we considered the following metrics:
\begin{itemize}
\item Root mean square error (RMSE)
\item Structural similarity index (SSIM)
\item Peak signal-to-noise ratio (PSNR)
\end{itemize}

The models predicted cleaned versions of the validation images (Figure 1), which were then compared to the groundtruth versions according to each metric. The average over all such metrics was taken and is displayed in Table 3.\\

Despite the models having been trained to minimize the mean squared error, they performed quite well on the RMSE, SSIM, and PSNR tasks. RMSE is a general indicator of the model's denoising efficacy, while PSNR specifically looks at distributed noise features like Gaussian noise; structural-similarity is less useful in this case because we weren't concerned with superresolution or other tasks, but we include it as a baseline for future work.\\

\section{Future Work}
\label{sec:orgc17a604}

\subsection{Tuning Augraphy}
\label{sec:orgede3362}
The Augraphy pipeline used to generate training data for the Augraphy model was given in \ref{sec:orgd8c063f}; no attempt was made to adjust the default settings for the augmentations used. Much of the data used in training contained an excessive amount of noise, making the image unreadable, as in Figure 2.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./images/3-6-augraphy.png}
\caption{\label{fig:org5c6d5b6}An example of the naive Augraphy-generated training data}
\end{figure}

Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters. We leave the production of a dataset for training a more competitive denoiser to the reader.

\subsection{Additional Techniques}
\label{sec:org91f73b0}
For brevity of page length and time, this article only includes experimental results for one model architecture trained on one dataset created with the Augraphy data augmentation tool. We plan to evaluate denoisers built with other architectures, particularly transformers (DenSformer, DiT, etc.)
and generative adversarial networks (e.g. CycleGAN). During the validation task, the naive Augraphy model adequately removed the page fold and wrinkle noise, but considerably degraded the foreground text. By comparison, the NoisyOffice model left more of the text untouched, but allowed more of the stain features to remain. The Augraphy model's performance suggests that better results may be achieved by an ensemble built from an Augraphy-trained denoiser followed by an inpainting model.\\

Human toil is needed to assemble initial datasets, and we thank the NoisyOffice group for their efforts; we are already working to generate realistic document images purely synthetically, and intend to release a library for that soon.

\subsection{An Augraphy Dataset}
\label{sec:orgcf7613c}
Privacy and security concerns typically preclude the assembly of large sets of modern document images: most documents are not intended for general viewing. The authors have searched often, for over a year, and have been unable to find decently-sized (>10 images) sets of modern document images, besides the NoisyOffice set. We intend to release an Augraphy-generated dataset [ShabbyPages cit] in the coming months.

\subsection{Augraphy Enhancements}
\label{sec:orgea8aa95}
Several upgrades to the Augraphy library itself are also planned.
\subsubsection{Scaling}
\label{sec:orgd598e64}
While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.

\subsubsection{Performance}
\label{sec:org4b779de}
The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware. Performance enhancements to the library are already underway, which will decrease pipeline execution time dramatically, enabling faster creation of larger datasets on more common hardware.

\section{Conclusion}
\label{sec:org38b91e1}
We presented Augraphy, an augmentation framework for generating realistic datasets of modern document images. Two other players in the same space were examined and found lacking for our purposes, motivating the creation of this library. We described creating an Augraphy-noised version of the NoisyOffice dataset, then compared some preliminary results obtained by training a convolutional U-Net on these datasets. Finally, we discussed some future directions for research, and the continued evolution of this tool. Augraphy is licensed under the MIT open source license, and readers are invited to participate in its development on GitHub.
\end{document}

### 2023-01-06 paper.tex
update paper style, results, image assets

--- 2023-01-04 augraphy_paper.tex
@@
-% Created 2023-01-04 Wed 14:12
-% Intended LaTeX compiler: pdflatex
-\documentclass[runningheads]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\documentclass[runningheads]{llncs}
 \usepackage{graphicx}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage{amsmath, amsthm, amsfonts, enumerate}
-\author{Alexander Groleau, Samay Maini, Jonathan Boarman}
-\date{\today}
+\usepackage[colorlinks]{hyperref}
+\hypersetup{
+    colorlinks = false,
+    linkbordercolor = {blue}
+}
+\usepackage{listings}
+\usepackage{courier}
+%\renewcommand\UrlFont{\color{blue}\rmfamily}
+\renewcommand{\floatpagefraction}{.8}%
+\begin{document}
+
 \title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
-\hypersetup{
- pdfauthor={Alexander Groleau, Samay Maini, Jonathan Boarman},
- pdftitle={Augraphy: An Augmentation Pipeline API for Modern Document Images},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
- pdflang={English}}
-\begin{document}
+\author{Alexander Groleau\inst{1,2} \and
+Kok Wei Chee\inst{1} \and
+Samay Maini\inst{1} \and
+Jonathan Boarman\inst{1}}
+
+\authorrunning{A. Groleau et al.}
+
+\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
+\and
+Left Associates LLC (\email{research@left.associates})}
 
@@
 
-\section{Abstract}
-\label{sec:orgb8a4f58}
+\begin{abstract}
 We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
@@
 The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.
+\end{abstract}
 
 \section{Introduction and Motivation}
-\label{sec:org1b677d2}
 Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\
@@
 However, collecting or otherwise determining a set of labels for training data is quite challenging.
-In the case of text documents, most real-world dirty documents \emph{can't} come with clean ground-truths.\\
+In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\
 
@@
 \section{NoisyOffice}
-\label{sec:orga476358}
-Few datasets exist for out-of-the-box use in training document-specific models.
-Many other datasets containing modern documents exist, but are designed for tasks like layout detection [RDCL2019 cit], content extraction [Tobacco 800 cit], or handwriting recognition [ICDAR2019-CROHME-TDF cit].
-In our investigations, the only publically available dataset we could find that was exclusively focused on digitally-generated documents was the NoisyOffice set [CASTRO-BLEDA].\\
+Many document-focused datasets exist, but most are designed for tasks like layout detection \cite{ref_RDCL2019}, content extraction \cite{ref_tobacco800}, or handwriting recognition \cite{ref_icdar}.
+the only publically-available dataset we could find that was exclusively focused on digitally-generated modern documents was NoisyOffice \cite{ref_NoisyOffice}.\\
 
-The NoisyOffice dataset [paper link] was created as for document manipulation and analysis model training and validation. NoisyOffice includes three types of image:
+This database \cite{ref_NoisyOfficeDatabase}, hosted on the UCI Machine Learning Repository \cite{ref_UCIMLR}, was created for training image processing filters, including denoisers and superresolution models.
+NoisyOffice includes three types of image:
+
 \begin{enumerate}
@@
 
-While assembling the NoisyOffice database was a great service in its own right — no other such set seems to have been published — the NoisyOffice set is very limited:\\
+Assembling the NoisyOffice database was a great service to the document analysis community, but for our purposes, the set is too limited:
 
@@
 \item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
-\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models
+\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models.
 \end{itemize}
 
-Rather than providing a direct answer to these, Augraphy does not (yet) generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis taskwhile relying on users to supply the ground truth images.
+Rather than providing a direct answer to these, Augraphy does not generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis task while relying on users to supply the ground truth images.
 
 \section{DocCreator}
-\label{sec:orgf17073e}
-In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator seeming to occupy that niche.\\
+In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator \cite{ref_DocCreator} seeming to occupy that niche.\\
 
@@
 
-While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \emph{modern} documents.
-Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in C++, making it unsuitable for use either in a data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration.
-More frustrating still, the software is buggy and crashes often, making even successfully generating a single augmented document image quite an ordeal.\\
-
-Augraphy was not designed with historical documents in mind, but neither did its design preclude that possibility. Instead, the focus is on modern documents generated at least in part digitally.
+While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \textit{modern} documents.
+Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in \texttt{C++}, making it unsuitable for use either in a semi-automated data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration.
 
 \section{Document Distortion, Theory \& Technique}
-\label{sec:org24682f8}
 Many approaches exist for adding features to an image, and many types of feature can be generated.
@@
 
-Some techniques exist for introducing these features into images of documents, including but not limited to the following:\\
+Some techniques exist for introducing these features into images of documents, including but not limited to the following:
 \begin{enumerate}
@@
 \section{Augraphy}
-\label{sec:org4a1c65c}
 We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\
@@
 Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-A brief description of each augmentation appears in a table in the next section.
+Figure 1 shows the individual phases of an example pipeline combining to produce a noised document image.
+\begin{figure}
+\includegraphics[width=\textwidth]{pipeline.png}
+\caption{Visualization of an Augraphy pipeline.} \label{fig1}
+\end{figure}
 
 \section{The Augraphy API}
-\label{sec:orgd64a7b1}
 The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy.
@@
 
-Modern frameworks for machine learning like \texttt{fastai} [Fastai: A Layered API for Deep Learning cit] aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility.
+Modern frameworks for machine learning like \texttt{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility.
 We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
@@
 Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
-
-\begin{verbatim}
+\begin{lstlisting}[language=Python]
 from augraphy import *
@@
 augmented_img = data["output"]
-\end{verbatim}
+\end{lstlisting}
 
 \subsection{Base}
-\label{sec:org1182db0}
 \texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself.
@@
 
-There are four "main sequence" classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality.
+There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality.
 Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.
@@
 \subsubsection{Augmentation}
-\label{sec:org73d5fe0}
 Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
@@
 \subsubsection{AugmentationResult}
-\label{sec:org6aeadfa}
-After an augmentation is applied, the output of its execution is stored in an AugmentationResult object and passed forward through the pipeline.
+After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
 These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.
@@
 \subsubsection{AugmentationSequence}
-\label{sec:org0192f11}
-A list of Augmentations -- together with the intent to apply those Augmentations in sequence -- determines an AugmentationSequence, which is itself both an Augmentation and callable.
-In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of Augmentation constructor calls which produce callable Augmentation objects of the various flavors explored in \hyperref[sec:orgea493da]{Augmentations}.
-AugmentationSequences are applied to the image during each of the \hyperref[sec:org6690404]{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
+A list of \texttt{Augmentation}s -- together with the intent to apply those Augmentations in sequence -- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
+In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in .
+\texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
 
 \subsubsection{AugmentationPipeline}
-\label{sec:org6690404}
 The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life.
@@
 
-The value added by the AugrapyPipeline class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an AugraphyPipeline application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
+The value added by the \texttt{AugrapyPipeline} class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
 This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.
@@
 \subsubsection{OneOf}
-\label{sec:orgb9ecb78}
 Real-world processes generally allow for objects to exist in multiple states over time.
-To model the possibility that a document image has undergone one and only one of a collection of Augmentations, we use OneOf, which simply selects one of those Augmentations from a given list, and uses this to modify the image.
+To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.
 
 \subsubsection{PaperFactory}
-\label{sec:org16fabe6}
-We often print on multiple sizes and kinds of paper, and out in the world we certainly \emph{encounter} such diverse documents.
+We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
 We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline.
@@
 \subsection{Augmentations}
-\label{sec:orgea493da}
 The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}.
-We have already included many such transforms in the standard library, and have also provided \hyperref[sec:org8b47a22]{tools} for easily building new augmentations and integrating them into the Augraphy workflow.\\
+We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\
 
@@
 
-Table 1 contains a list of augmentations and a description of their simulated effects.
+Figures 2 and 3 contain representative images of each augmentation applied to this very document.
+Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.
 
-\begin{center}
-\begin{tabular}{ll}
-Augmentation & Effect\\
-\hline
-BadPhotoCopy & Regions of noise and shadow like those produced by a dirty photocopier.\\
-BindingsAndFasteners & Staples, paper clips, punched holes, and other results of physical tools applied to a document.\\
-BleedThrough & Ink bleeding through the page from the reverse side.\\
-BookBinding & The page curling away from the scanner bed, towards the binding of a book or magazine.\\
-Brightness & Adjusts the brightness of the whole image by a chosen multiplier.\\
-BrightnessTexturize & Random noise in the brightnes channel of the image, which emulates various paper textures.\\
-DirtyDrum & Deposits of dirt and ink-grime from dirty printer drums.\\
-DirtyRollers & Dirty document scanners can leave roller lines on the page.\\
-Dithering & Ordered or Floyd-Steinberg dithering is applied to simulate downsampling during document processing.\\
-DustyInk & Random noise in the ink emulates dusty or inconsistent ink tone when combined with a blur.\\
-Faxify & Faxing documents introduces artifacts related to errors in transmission.\\
-Folding & Folded paper exhibits a visible warp effect around the folding axis\\
-Gamma & Gamma controls several features, particularly relative brightness and contrast\\
-Geometric & Basic spatial transformations like resizing, flipping, and rotation\\
-Inkbleed & Creates a fuzzy edge emulating over-application of ink during printing.\\
-Jpeg & JPEG compression artifacts (deep fry your documents!)\\
-Letterpress & Regions of ink pressed unevenly onto paper by a printing press\\
-LightingGradient & Introduces a shading pattern over the document, like a photograph with a partially-occluded light source\\
-LowInkBlobs & When a printer's ink supply is low, some areas of prints receive less ink in spots than they should.\\
-LowInkPeriodicLines & A set of parallel lines that repeat in a periodic fashion throughout the image.\\
-LowInkRandomLines & A set of parallel lines randomly distributed throughout the image.\\
-Markup & Adds strikethrough, highlighting, or underline effects to the text.\\
-NoiseTexturize & Another method of emulating different paper textures, by introducing Gaussian noise into the paper layer.\\
-PageBorder & Simulates the edges of background pages on one side of the foreground page.\\
-PencilScribbles & Random pencil marks, like the product of an idle student.\\
-SubtleNoise & Using a document scanner to digitize a page introduces imperfections in solid regions due to subtle lighting differences.\\
-\end{tabular}
-\end{center}
+\begin{figure}
+\includegraphics[width=\textwidth]{augmentations1.png}
+\caption{Examples of each augmentation.} \label{fig2}
+\end{figure}
 
-\subsection{Utilities}
-\label{sec:org8b47a22}
-Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience during use in unforseen contexts, such as with other libraries.
+\begin{figure}
+\includegraphics[width=\textwidth]{augmentations2.png}
+\caption{Examples of each augmentation.} \label{fig3}
+\end{figure}
 
-\begin{center}
-\begin{tabular}{ll}
-Class & Purpose\\
-\hline
-ComposePipelines & Provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.\\
-FigshareDownloader & Functions to query and download files from Figshare, a popular online repository of research data.\\
-Foreign & Provides a means of wrapping augmentations from other projects, like Albumentations and imgaug.\\
-Function & Wraps an arbitrary Python function or a list of such functions into an augmentation.\\
-ImageOverlay & Places a given foreground image onto a given background, either randomly or at a specified location.\\
-NoiseGenerator & Generates noise masks for placement on other images or in implementations of other augmentations.\\
-OverlayBuilder & Creates an image mask containing other images, like hole punches or binder clips, for overlay onto a document.\\
-\end{tabular}
-\end{center}
+\subsection{Utilities}\label{utilities}
+Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience.
+Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively
 
+\begin{enumerate}
+\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
+\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
+\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
+\end{enumerate}
 \section{Deep Learning with Augraphy}
-\label{sec:org4d4729d}
 Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
 This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data.
-The NoisyOffice team set a baseline for others to follow in ["The NoisyOffice Database: A corpus to train supervised machine learning filters for image processing" CASTRO-BLEDA].
-We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate set for Augraphy analysis.\\
-
-Models were trained on an NVidia A100 GPU on Google Colaboratory. All preprocessing, training, and testing was done from a Jupyter notebook, published on GitHub.
+We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for Augraphy analysis.
 
 \subsection{Model Architecture}
-\label{sec:org83264cc}
 To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library.
-This network achieved a high score on the NoisyOffice Kaggle competition [citation for Michal Brezák's notebook on Kaggle \url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}]; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
-For more exploration of models trained to solve this competition's challenge, see Colin Priest's work here: [citation for Colin Priest \url{https://colinpriest.com/2015/11/15/an-even-dozen-denoising-dirty-documents-part-12/}].\\
+This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.\\
 
-This low-layer model contains two layers of a convolution, each followed by a ReLU activation function, then a batch normalization layer as the encoding step.
+This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step.
 After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively.
@@
 \subsection{Data Generation}
-\label{sec:orgd8c063f}
 Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\
@@
 
-\begin{verbatim}
+\begin{lstlisting}
 ink_phase = []
@@
 AugraphyPipeline(ink_phase, paper_phase, post_phase)
-\end{verbatim}
-
-Generating these 1440 images took 35 seconds with the rendering job spread across the 64 cores of an AWS c7g.16xlarge instance.
-
+\end{lstlisting}
 \subsection{Training Regime}
-\label{sec:org4144ef4}
 We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\
@@
 
-Both models were trained with mean squared error as the loss function, using the Adam optimizer.\\
+Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.
 
-The NoisyOffice model finished training with an average loss of 0.0010, a mean average error of 0.0150, validation loss of 7.4609e-04, validation mean average error of 0.0122.
-Training took an average of 190ms/step and 1s/epoch.\\
-
-The Augraphy model finished training with an average loss of 0.0014, a mean average error of 0.0142, validation loss of 8.9985e-04, and validation mean average error of 0.0112.
-Training took roughly 218ms/step and 11s/epoch.
+\begin{table}
+\centering
+\caption{Model training statistics}\label{tab1}
+\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
+\hline
+Model & NoisyOffice & Augraphy\\
+\hline
+Average Loss & 0.0010 & 0.0014\\
+Mean Average Error & 0.0150 & 0.0142\\
+Validation Loss & 7.4609e-04 & 8.9985e-04\\
+Validation Mean Average Error & 0.0122 & 0.0112\\
+Training Time & 190ms/step & 218ms/step\\
+\hline
+\end{tabular}
+\end{table}
 
 \subsection{Results}
-\label{sec:org9fa72d2}
 Sample predictions from each model on the validation task are presented in Figure 1.
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./images/sidebyside.png}
-\caption{\label{fig:org74839c0}Comparison of the validation image (left) and the images predicted by the NoisyOffice model (center) and Augraphy model (right)}
+\begin{figure}\label{fig4}
+\includegraphics[width=\textwidth]{sidebyside.png}
+\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.} \label{fig4}
 \end{figure}
@@
 To compare the models' performance on the validation task, we considered the following metrics:
-\begin{itemize}
+\begin{enumerate}
 \item Root mean square error (RMSE)
@@
 \item Peak signal-to-noise ratio (PSNR)
-\end{itemize}
+\end{enumerate}
 
-The models predicted cleaned versions of the validation images (Figure 1), which were then compared to the groundtruth versions according to each metric.
-The average over all such metrics was taken and is displayed in Table 3.\\
+The models predicted cleaned versions of the validation images (\ref{fig4}), which were then compared to the groundtruth versions according to each metric.
+The average over all such results was taken and is displayed in Table 2.
+
+\begin{table}
+\centering
+\caption{Model performance on NoisyOffice validation task}\label{tab1}
+\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
+\hline
+Model &  Metric & Average value\\
+\hline
+NoisyOffice & PSNR & 63.09152246942623\\
+Augraphy & PSNR & 63.11842705899114\\
+NoisyOffice & SSIM & 0.8726093605602885\\
+Augraphy & SSIM & 0.8633782608031118\\
+NoisyOffice & RMSE & 0.1878745854176291\\
+Augraphy & RMSE & 0.1866188481559681\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \section{Future Work}
-\label{sec:orgc17a604}
+This section describes new directions for research and development.
 
 \subsection{Tuning Augraphy}
-\label{sec:orgede3362}
-The Augraphy pipeline used to generate training data for the Augraphy model was given in \ref{sec:orgd8c063f}; no attempt was made to adjust the default settings for the augmentations used.
-Much of the data used in training contained an excessive amount of noise, making the image unreadable, as in Figure 2.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./images/3-6-augraphy.png}
-\caption{\label{fig:org5c6d5b6}An example of the naive Augraphy-generated training data}
-\end{figure}
-
+The Augraphy pipeline used to generate training data for the Augraphy model was extremely naive, and only contained two augmentations; no attempt was made to adjust the default settings, demonstrating Augraphy's high degree of both utility and ease-of-use.
+Much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from.
 Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters.
-We leave the production of a dataset for training a more competitive denoiser to the reader.
 
 \subsection{Additional Techniques}
-\label{sec:org91f73b0}
-For brevity of page length and time, this article only includes experimental results for one model architecture trained on one dataset created with the Augraphy data augmentation tool.
-We plan to evaluate denoisers built with other architectures, particularly transformers (DenSformer, DiT, etc.)
-and generative adversarial networks (e.g.
-CycleGAN).
+For brevity of both page length and time, this article only includes experimental results for one type of model.
+We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion models, generative adversarial networks, and ensembles of these.
 During the validation task, the naive Augraphy model adequately removed the page fold and wrinkle noise, but considerably degraded the foreground text.
 By comparison, the NoisyOffice model left more of the text untouched, but allowed more of the stain features to remain.
-The Augraphy model's performance suggests that better results may be achieved by an ensemble built from an Augraphy-trained denoiser followed by an inpainting model.\\
+The Augraphy model's performance suggests that better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model.\\
 
-Human toil is needed to assemble initial datasets, and we thank the NoisyOffice group for their efforts; we are already working to generate realistic document images purely synthetically, and intend to release a library for that soon.
+Human toil is needed to assemble initial datasets.
+To alleviate this, we are developing another library for generating document images purely synthetically, and intend to release a library for that soon.
 
 \subsection{An Augraphy Dataset}
-\label{sec:orgcf7613c}
 Privacy and security concerns typically preclude the assembly of large sets of modern document images: most documents are not intended for general viewing.
-The authors have searched often, for over a year, and have been unable to find decently-sized (>10 images) sets of modern document images, besides the NoisyOffice set.
-We intend to release an Augraphy-generated dataset [ShabbyPages cit] in the coming months.
+The authors have searched frequently, for over a year, and have been unable to find decently-sized (>10 images) sets of modern document images, besides the NoisyOffice set.
+We intend to release an Augraphy-generated dataset in the coming months.
 
 \subsection{Augraphy Enhancements}
-\label{sec:orgea8aa95}
 Several upgrades to the Augraphy library itself are also planned.
+
 \subsubsection{Scaling}
-\label{sec:orgd598e64}
 While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.
@@
 \subsubsection{Performance}
-\label{sec:org4b779de}
 The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware.
@@
 \section{Conclusion}
-\label{sec:org38b91e1}
 We presented Augraphy, an augmentation framework for generating realistic datasets of modern document images.
@@
 Augraphy is licensed under the MIT open source license, and readers are invited to participate in its development on GitHub.
+
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
+\begin{thebibliography}{8}
+\bibitem{ref_RDCL2019}
+{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
+
+\bibitem{ref_tobacco800}
+{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
+
+\bibitem{ref_icdar}
+{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
+
+\bibitem{ref_NoisyOffice}
+{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ.
+(2020).
+The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing.
+The Computer Journal.
+63(11):1658-1667.
+https://doi.org/10.1093/comjnl/bxz098}
+
+\bibitem{ref_NoisyOfficeDatabase}
+{F.
+Zamora-Martinez, S.
+España-Boquera and M.
+J.
+Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
+
+\bibitem{ref_UCIMLR}
+{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
+
+\bibitem{ref_DocCreator}
+  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
+
+\bibitem{ref_fastai}
+{Jeremy Howard and Sylvain Gugger, Fastai: A Layered API for Deep Learning. Information 2020, 2, 11}
+
+\bibitem{ref_albumentations}
+{Alexander Buslaev, Vladimir I.
+Iglovikov, Eugene Khvedchenya, Alex Parinov, Mikhail Druzhinin, and Alexandr A.
+Kalinin.
+Albumentations: Fast and flexible image augmentations.
+Information, 11(2), 2020.}
+
+\bibitem{ref_imgaug}
+{Alexander B.
+Jung, Kentaro Wada, Jon Crall, Satoshi Tanaka, Jake Graving, Christoph Reinders, Sarthak Yadav, Joy Banerjee, Gabor Vecsei, Adam Kraft, Zheng Rui, Jirka Borovec, Christian Vallentin, Semen Zhydenko, Kilian Pfeiffer, Ben Cook, Ismael Fernandez, Francois-Michel De Rainville, Chi-Hung Weng, Abner Ayala-Acevedo, Raphael Meudec, Matias Laporte, et al.
+imgaug.
+https://github.com/aleju/imgaug, 2020.
+Online; accessed 01-Feb-2020.}
+\end{thebibliography}
 \end{document}

### 2023-01-10 paper.tex
add new model training and results metrics and discussion

@@
 \usepackage{courier}
-%\renewcommand\UrlFont{\color{blue}\rmfamily}
-\renewcommand{\floatpagefraction}{.8}%
+\renewcommand{\floatpagefraction}{.8}
+%
 \begin{document}
@@
 A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy.
-The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.
+The library is used to quickly produce a derivative of the NoisyOffice dataset, on which a simple convolutional neural network is trained, which on some metrics outperforms the same network trained on the NoisyOffice set; the results of this experiment are discussed, followed by a look forward to further anticipated work.
 \end{abstract}
@@
 \section{Introduction and Motivation}
-Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\
-
+Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.
 Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths.
@@
 The NoisyOffice dataset contains folded sheets, wrinkled sheets, coffee stains, and footprint noise.
-The features given by the wrinkle and fold distortions can be mimicked with some Gaussian noise applied at various points along a line, and the features created by the stains and footprints can be mimicked with dark regions and thin lines.
-With Augraphy, we expected that we could use the BadPhotoCopy augmentation and the strikethrough behavior from the Markup augmentation to add these features to the ground-truth data, so we executed the following pipeline:
+The features given by the wrinkle and fold distortions can be mimicked by overlaying the foreground text on wrinkled and folded paper textures, as the NoisyOffice team did, and the features created by the stains and footprints can be mimicked by introducing dark regions and thin lines.
+With Augraphy, we expected that we could use the BadPhotoCopy augmentation to produce the dark regions and a combination of the strikethrough behavior from the Markup augmentation and the smooth curve shading behavior of the PencilScribbles augmentation to add the last feature to the ground-truth data.
+The PaperFactory augmentation makes the paper texture overlay trivial and repeatable.
+In the end, we executed the following pipeline:
 
@@
 ink_phase = []
-paper_phase = []
-post_phase = [BadPhotoCopy(), Markup()]
+paper_phase = [PaperFactory(p=0.5)]
+post_phase = [
+  BadPhotoCopy(p=0.5),
+  PencilScribbles(p=0.5),
+  Markup(markup_color=(0,0,0), p=0.5)
+]
 
@@
 \end{lstlisting}
+
+In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.\\
+
+The PaperFactory augmentation reads and randomly crops image textures from a local directory; to this we added two \footnote{\url{https://p2.piqsels.com/preview/642/889/110/paper-crease-creased-texture.jpg
+}}, \footnote{\url{https://blog.miklavcic.si/wp-content/uploads/2011/11/white_paper_1.png}} public domain images of wrinkled paper found on Bing.
+
 \subsection{Training Regime}
@@
 Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.
-
-\begin{table}
-\centering
-\caption{Model training statistics}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
-\hline
-Model & NoisyOffice & Augraphy\\
-\hline
-Average Loss & 0.0010 & 0.0014\\
-Mean Average Error & 0.0150 & 0.0142\\
-Validation Loss & 7.4609e-04 & 8.9985e-04\\
-Validation Mean Average Error & 0.0122 & 0.0112\\
-Training Time & 190ms/step & 218ms/step\\
-\hline
-\end{tabular}
-\end{table}
 
@@
 
-The models predicted cleaned versions of the validation images (\ref{fig4}), which were then compared to the groundtruth versions according to each metric.
-The average over all such results was taken and is displayed in Table 2.
+Over the last 5 epochs of training, the performance of the models on average loss, average mean-average-error (MAE), average validation loss, and average validation MAE were recorded.
+The models predicted cleaned versions of the validation images (Figure 4), which were then compared to the groundtruth versions according to each metric.
+The average over all such results obtained during validation was taken.
+These metrics are displayed in Table 1.
 
@@
 \centering
-\caption{Model performance on NoisyOffice validation task}\label{tab1}
+\caption{Model training statistics and performance on NoisyOffice validation task}\label{tab1}
 \begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
 \hline
-Model &  Metric & Average value\\
+Metric & NoisyOffice & Augraphy\\
 \hline
-NoisyOffice & PSNR & 63.09152246942623\\
-Augraphy & PSNR & 63.11842705899114\\
-NoisyOffice & SSIM & 0.8726093605602885\\
-Augraphy & SSIM & 0.8633782608031118\\
-NoisyOffice & RMSE & 0.1878745854176291\\
-Augraphy & RMSE & 0.1866188481559681\\
+PSNR & 63.09152246942623 & 63.3491691640664\\
+SSIM & 0.8726093605602885 & 0.8662918306486613\\
+RMSE & 0.1878745854176291 & 0.18310202817380003\\
+Test Loss & 0.0011 & 0.0012\\
+Test MAE & 0.0150 & 0.0129\\
+Validation Loss & 7.5551e-04 & 8.22202e-04\\
+Validation MAE & 0.01236 & 0.01076\\
+Training Time & 190ms/step & 218ms/step\\
 \hline
@@
 
-Despite the models having been trained to minimize the mean squared error, they performed quite well on the RMSE, SSIM, and PSNR tasks.
-RMSE is a general indicator of the model's denoising efficacy, while PSNR specifically looks at distributed noise features like Gaussian noise; structural-similarity is less useful in this case because we weren't concerned with superresolution or other tasks, but we include it as a baseline for future work.\\
+The Augraphy model outperforms the PSNR score of the NoisyOffice model on the validation task by half a percent, and has a lower mean average error both in test and validation during training, but underperforms by 0.8\% on structural similarity and 2.5\% on RMSE in validation, with a higher average test and validation loss.
+These numbers are consistent with the visual prediction results displayed in Figure 1: the Augraphy model predicts fewer pixels in the text (RMSE lower by 2.5\%), but removes more noise and with a higher degree of fidelity than the NoisyOffice model (PSNR higher by 0.2576466946).
+The training metrics collected indicate that the Augraphy model has lower variance so is more precise than the NoisyOffice model, but exhibits higher loss and thus less accuracy in its predictions.
 
@@
 
-\subsection{Tuning Augraphy}
-The Augraphy pipeline used to generate training data for the Augraphy model was extremely naive, and only contained two augmentations; no attempt was made to adjust the default settings, demonstrating Augraphy's high degree of both utility and ease-of-use.
-Much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from.
-Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters.
+\subsection{Tuning the Pipeline}
+The pipeline used to generate training data for the Augraphy model was extremely naive, and only contained four augmentations, most with default parameters, demonstrating Augraphy's high degree of both utility and ease-of-use.
+However, much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from.
+Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters to generate training images closer to the validation set.
 
 \subsection{Additional Techniques}
-For brevity of both page length and time, this article only includes experimental results for one type of model.
-We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion models, generative adversarial networks, and ensembles of these.
-During the validation task, the naive Augraphy model adequately removed the page fold and wrinkle noise, but considerably degraded the foreground text.
-By comparison, the NoisyOffice model left more of the text untouched, but allowed more of the stain features to remain.
-The Augraphy model's performance suggests that better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model.\\
-
-Human toil is needed to assemble initial datasets.
-To alleviate this, we are developing another library for generating document images purely synthetically, and intend to release a library for that soon.
+For brevity, this article only includes experimental results for one type of model.
+We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion and generative adversarial networks, and ensembles of these.
+During the validation task, the naive Augraphy model correctly removed the page fold and wrinkle noise, but visually degraded regions of the foreground text.
+By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output.
+Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.\\
 

### 2023-01-15 paper.tex
update bibliography w bibtex

@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{8}
-\bibitem{ref_RDCL2019}
-{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
+\bibliographystyle{splncs04}
+\bibliography{paper}
 
-\bibitem{ref_tobacco800}
-{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
-
-\bibitem{ref_icdar}
-{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
-
-\bibitem{ref_NoisyOffice}
-{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ.
-(2020).
-The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing.
-The Computer Journal.
-63(11):1658-1667.
-https://doi.org/10.1093/comjnl/bxz098}
-
-\bibitem{ref_NoisyOfficeDatabase}
-{F.
-Zamora-Martinez, S.
-España-Boquera and M.
-J.
-Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
-
-\bibitem{ref_UCIMLR}
-{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
-
-\bibitem{ref_DocCreator}
-  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
-
-\bibitem{ref_fastai}
-{Jeremy Howard and Sylvain Gugger, Fastai: A Layered API for Deep Learning. Information 2020, 2, 11}
-
-\bibitem{ref_albumentations}
-{Alexander Buslaev, Vladimir I.
-Iglovikov, Eugene Khvedchenya, Alex Parinov, Mikhail Druzhinin, and Alexandr A.
-Kalinin.
-Albumentations: Fast and flexible image augmentations.
-Information, 11(2), 2020.}
-
-\bibitem{ref_imgaug}
-  {Alexander B.
-Jung, Kentaro Wada, Jon Crall, Satoshi Tanaka, Jake Graving, Christoph Reinders, Sarthak Yadav, Joy Banerjee, Gabor Vecsei, Adam Kraft, Zheng Rui, Jirka Borovec, Christian Vallentin, Semen Zhydenko, Kilian Pfeiffer, Ben Cook, Ismael Fernandez, Francois-Michel De Rainville, Chi-Hung Weng, Abner Ayala-Acevedo, Raphael Meudec, Matias Laporte, et al.
-imgaug.
-https://github.com/aleju/imgaug, 2020.
-Online; accessed 01-Feb-2020.}
-\end{thebibliography}
 \end{document}

### 2023-01-15 paper.tex
anonymize to be double-blind
re-work related work section

--- 2023-01-10 paper.tex
@@
 \usepackage{courier}
+\usepackage{booktabs}
+\usepackage[dvipsnames]{xcolor}
+\usepackage{amssymb}
+\usepackage{pifont}
 \renewcommand{\floatpagefraction}{.8}
+
+% check mark and x for table
+\newcommand{\cmark}{{\color{ForestGreen}\ding{51}}}%
+\newcommand{\xmark}{{\color{Maroon}\ding{55}}}%
+
+\newcommand{\numAugraphyAugmentations}{\emph{n}}
+
 %
@@
 
-\section{NoisyOffice}
-Many document-focused datasets exist, but most are designed for tasks like layout detection \cite{ref_RDCL2019}, content extraction \cite{ref_tobacco800}, or handwriting recognition \cite{ref_icdar}.
+\begin{table}[]
+    \centering
+    \caption{Comparison of various image-based data augmentation libraries.}
+    \scalebox{0.9}{
+    \begin{tabular}{lccccc}
+    \toprule
+        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
+        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
+    \midrule
+        \emph{Augmentor} \cite{augmentor} & & \xmark &  & \cmark & MIT \\ 
+        \emph{Albumentations} \cite{ref_albumentations} &  & \xmark & \cmark & \cmark & MIT \\
+        \emph{imgaug} \cite{ref_imgaug} & & \xmark & \cmark & \cmark & MIT \\
+        \emph{Augly} \cite{Papakipos2022-gq-augly} & & \xmark & & \cmark & MIT \\
+        \emph{Pytorch} \cite{pytorch} & & \xmark & \cmark & \cmark & BSD-style \\
+        \emph{DocCreator} \cite{ref_DocCreator} & & \cmark & \xmark & \xmark & LGPL-3.0 \\
+        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
+    \bottomrule
+    \end{tabular}}
+    \label{tab:augmentation-library-comparison}
+\end{table}
+
+\section{Related Work}
+
+%This section discusses prior work related to document data augmentation, robustness testing, and document de-noising.
+This section discusses prior work related to data augmentation and robustness testing, especially as it relates to document understanding and processing tasks.
+
+\subsection{Data Augmentation}
+A wide variety of data augmentation tools and pipelines exist for machine learning tasks ranging from natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
+In the image realm of image processing and computer vision, data augmentation tools and pipelines include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, Pytorch \cite{pytorch}, and \emph{imgaug} \cite{ref_imgaug}.
+Augmentation strategies from these image-centric libraries are typically general purpose, and include image transformations like rotations, warps, and color modifications.
+Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image-based data augmentation libraries and tools.
+As can be seen, these other data augmentation libraries do not specifically provide support for imitating the corruptions commonly seen in document analysis corpora.
+
+A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
+\emph{DocCreator} differs from \emph{Augraphy} in several ways, however.
+The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is meant to replicate noise caused by noisy office room procedures.
+\emph{DocCreator} is also written in the C++ programming language and is a monolithic what-you-see-is-what-you-get (WYSIWYG) tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
+\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, and can easily be used alongside other Python packages.
+
+\subsection{Robustness Testing}
+
+The introduction of noise-like corruptions and other modifications to image data can be used as a way of estimating and evaluating model robustness.
+Prior work in this space includes the use of image blurring, contrast and brightness changes, color alterations, partial occlusions, geometric transformations, pixel-level noise (e.g., salt-and-pepper noise, impulse noise, etc.), and compression artefacts (e.g., JPEG) to evaluate image classification and object detection models (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
+More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
+Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications.
+
+%\section{NoisyOffice}
+%Many document-focused datasets exist, but most are designed for tasks like layout detection \cite{ref_RDCL2019}, content extraction \cite{ref_tobacco800}, or handwriting recognition \cite{ref_icdar}.
 the only publically-available dataset we could find that was exclusively focused on digitally-generated modern documents was NoisyOffice \cite{ref_NoisyOffice}.\\
-
-This database \cite{ref_NoisyOfficeDatabase}, hosted on the UCI Machine Learning Repository \cite{ref_UCIMLR}, was created for training image processing filters, including denoisers and superresolution models.
+%
+%This database \cite{ref_NoisyOfficeDatabase}, hosted on the UCI Machine Learning Repository \cite{ref_UCIMLR}, was created for training image processing filters, including denoisers and superresolution models.
 NoisyOffice includes three types of image:
-
-\begin{enumerate}
-\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
-\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
-\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
-\end{enumerate}
-
-Assembling the NoisyOffice database was a great service to the document analysis community, but for our purposes, the set is too limited:
-
-\begin{itemize}
-\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
-\item the text is all English-language
-\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
-\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models.
-\end{itemize}
-
-Rather than providing a direct answer to these, Augraphy does not generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis task while relying on users to supply the ground truth images.
-
-\section{DocCreator}
-In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator \cite{ref_DocCreator} seeming to occupy that niche.\\
-
-DocCreator contains character-set-level distortions, a mechanism for overlaying characters onto an arbitrary paper texture akin to merge technique \#1, and also includes an experimental tool for fusing the document image onto one of several 3D meshes to simulate physical alterations to the document like a crumpled and smoothed page.\\
-
-While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \textit{modern} documents.
+%
+%\begin{enumerate}
+%\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
+%\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
+%\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
+%\end{enumerate}
+%
+%Assembling the NoisyOffice database was a great service to the document analysis community, but for our purposes, the set is too limited:
+%
+%\begin{itemize}
+%\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
+%\item the text is all English-language
+%\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
+%\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models.
+%\end{itemize}
+%
+%Rather than providing a direct answer to these, Augraphy does not generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis task while relying on users to supply the ground truth images.
+%
+%\section{DocCreator}
+%In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator \cite{ref_DocCreator} seeming to occupy that niche.\\
+%
+%DocCreator contains character-set-level distortions, a mechanism for overlaying characters onto an arbitrary paper texture akin to merge technique \#1, and also includes an experimental tool for fusing the document image onto one of several 3D meshes to simulate physical alterations to the document like a crumpled and smoothed page.\\
+%
+%While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \textit{modern} documents.
 Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in \texttt{C++}, making it unsuitable for use either in a semi-automated data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration.

### 2023-01-16 paper.tex
changes to abstract

--- 2023-01-10 paper.tex
@@
 \begin{abstract}
-We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
+%We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
 A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy.
 The library is used to quickly produce a derivative of the NoisyOffice dataset, on which a simple convolutional neural network is trained, which on some metrics outperforms the same network trained on the NoisyOffice set; the results of this experiment are discussed, followed by a look forward to further anticipated work.
+This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
+Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
+This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
 \end{abstract}

### 2023-01-16 paper.tex
adding keywords

--- 2023-01-15 paper.tex
@@
 \title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
-\author{Alexander Groleau\inst{1,2} \and
-Kok Wei Chee\inst{1} \and
-Samay Maini\inst{1} \and
-Jonathan Boarman\inst{1}}
+%\author{Alexander Groleau\inst{1,2} \and
+%Kok Wei Chee\inst{1} \and
+%Samay Maini\inst{1} \and
+%Jonathan Boarman\inst{1}}
+%
+%\authorrunning{A. Groleau et al.}
+%
+%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
+%\and
+%Left Associates LLC (\email{research@left.associates})}
 
-\authorrunning{A. Groleau et al.}
-
-\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
-\and
-Left Associates LLC (\email{research@left.associates})}
+\author{Anonymous ICDAR 2023 submission}
 

### 2023-01-16 paper.tex
add more to introduction

--- 2023-01-16 paper.tex
@@
 \begin{abstract}
-%We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
+We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
 A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy.
 The library is used to quickly produce a derivative of the NoisyOffice dataset, on which a simple convolutional neural network is trained, which on some metrics outperforms the same network trained on the NoisyOffice set; the results of this experiment are discussed, followed by a look forward to further anticipated work.
-This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
-Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
 \end{abstract}
@@
 \section{Introduction and Motivation}
-Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.
+%Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.
 Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths.
@@
 In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\
-
-Most often, source documents are too old, and often were created before the advent of digital storage media.
+%
+%Most often, source documents are too old, and often were created before the advent of digital storage media.
 Some documents are one-offs, produced ad-hoc in the typewriter era, but many more still were printed directly from the text editor used to write them, with no copy saved even after it became possible to do so.
@@
 For these reasons, it's much easier to take clean documents and add distorting features to them with a tool like Augraphy than to start with the warped images and find or create ground-truths.
+
+The modern world provides a plethora of tasks that require the need for automated and intelligent solutions for handling unstructured data.
+Often, this data is in the form of documents, and these documents may appear noisy, especially if they have been captured from the physical world via printing, scanning, or photocopying processes.
+Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human annotations like highlighting or pencil marks can add noise to the page.
+
+Many tasks involving machine learning are impacted by document noise.
+High-level tasks like document classification and information extraction must often be able to perform on noisily scanned document images.
+For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
+Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
+Further, the lower-level task of document de-noising tackles the document noise problem more directly by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
+Such tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.
+
+\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
+\centering
+\fbox{
+    \begin{minipage}{2in}
+        \hfill\vspace{1in}
+    \end{minipage}
+    }
+\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
+\end{figure}
+
+For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office room procedures.
+\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
+\emph{Augraphy} offers \numAugraphyAugmentations~ individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
+The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~X and in Figure~Y.
+This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.
 

### 2023-01-16 paper.tex

--- 2023-01-16 paper.tex
@@
 \begin{abstract}
-We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks.
-A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy.
-The library is used to quickly produce a derivative of the NoisyOffice dataset, on which a simple convolutional neural network is trained, which on some metrics outperforms the same network trained on the NoisyOffice set; the results of this experiment are discussed, followed by a look forward to further anticipated work.
+This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
+Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
+This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
+
 \end{abstract}

### 2023-01-17 paper.tex
fix image label, fix bibliography brackets, update pdf

@@
 \usepackage{pifont}
+\usepackage{listings}
+\usepackage{times}
 \renewcommand{\floatpagefraction}{.8}
@@
 \newcommand{\xmark}{{\color{Maroon}\ding{55}}}%
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+\lstset{style=mystyle}
 
@@
 \section{Augraphy}
-We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\
+This section dives into detail about the \emph{Augraphy} library.
+We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
 
-The library contains 18 unique transformations — augmentations, in Augraphy's parlance — which may be sequenced into a pipeline object which carries out the image manipulation.
-Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.\\
+\subsection{Overview}
 
-Augraphy attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
-The ink phase exists to sequence effects which specifically alter the printed ink — like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time — and transform them prior to "printing".
-The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here we find the PaperFactory generator for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
+\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
+It is registered on the Python Package Index (PyPI) and can be installed using
+\begin{center}
+\textbf{\texttt{pip install augraphy}}
+\end{center}
+\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}.
+\emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments.
+Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
+%Examples of output generated by \emph{Augraphy} are shown in Figure~\ref{fig:augraphy_examples_3x5}.
+
+\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Transforming an image with \emph{Augraphy}.}]
+import augraphy; import cv2
+pipeline = augraphy.default_augraphy_pipeline()
+img = cv2.imread("image.png")
+data = pipeline.augment(img)
+augmented = data["output"]
+\end{lstlisting}
+Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
+%We wanted the library
+The library is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
+The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
+
+%We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\
+
+\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into a pipeline object that carries out the image manipulation.
+Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
+\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
+The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".
+
+The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator is utilized for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
 After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-After "printing", the document enters the post-phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
+After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
 Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-Figure 1 shows the individual phases of an example pipeline combining to produce a noised document image.
+Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
+
 \begin{figure}
-\includegraphics[width=\textwidth]{pipeline.png}
-\caption{Visualization of an Augraphy pipeline.} \label{fig1}
+\centering
+\scalebox{0.33}{
+\includegraphics[]{pipeline.png}}
+\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
 \end{figure}
 
-\section{The Augraphy API}
-The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy.
-When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented datasets.\\
+\subsection{Augraphy Augmentations}
 
-Modern frameworks for machine learning like \texttt{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility.
-We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
-The default Augraphy pipeline makes use of all of the augmentations available in Augraphy, with starting parameters selected after manual visual inspection of several thousand images.
-Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
-\begin{lstlisting}[language=Python]
-from augraphy import *
-pipeline = default_augraphy_pipeline()
-img = cv2.imread("image.png")
-data = pipeline.augment(img)
-augmented_img = data["output"]
-\end{lstlisting}
+Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
+These augmentations are listed in Table~\ref{tab:augmentations}.
+As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
+These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
+Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.
 
-\subsection{Base}
-\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself.
+Augmentations provided by the Paper Phase include \texttt{BrightnessTexturize}, which introduces random noise in the brightness channel to emulate paper textures, and \texttt{Watermark}, which imitates watermarks in a piece of paper.
+Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
+These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates a book binding effect with shadow and curved lines to imitate how a page from a book might appear after being scanned with a flatbed scanner.
+Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations as well.
+Descriptions of- and motivation for each augmentation are available on GitHub. \footnote{\url{https://github.com/sparkfish/augraphy}}
+% TODO: is there a more precise link for these descriptions?
+
+%Augraphy is designed to replicate noise-like effects seen in real-world documents, and the library's
+%, so each augmentation represents a feature that will appear in the final dataset.
+%augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
+%Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well.
+The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\
+
+% TODO: I don't think this table is entirely correct, some augmentations might be listed in the wrong columns
+\begin{table}[]
+    \centering
+    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase.}
+    \scalebox{0.81}{
+    \begin{tabular}{lll}
+    \toprule
+        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} \\
+        \midrule
+        \textsf{BleedThrough} & \textsf{BrightnessTexturize} & \textsf{BadPhotoCopy} \\
+        \textsf{DirtyDrum} & \textsf{ColorPaper} & \textsf{BindingsAndFasteners} \\
+        \textsf{DirtyRollers} & \textsf{Gamma} & \textsf{BookBinding} \\
+        \textsf{Dithering} & \textsf{Geometric} & \textsf{Folding} \\
+        \textsf{Faxify} & \textsf{LightingGradient} & \textsf{JPEG} \\
+        \textsf{InkBleed} & \textsf{PageBorder} & \textsf{NoiseTexturize} \\
+        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{Watermark} \\
+        \textsf{LowInkLine} & & \\
+        \textsf{Markup} & & \\
+        \textsf{PencilScribbles} & & \\
+        \bottomrule
+    \end{tabular}}
+    \label{tab:augmentations}
+\end{table}
+
+\subsection{The Augraphy Library}
+\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners,
+%The library was developed in Python, to allow maximal accessibility for practitioners,
+and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
+When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented document images.
+
+%Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
+%We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
+%The default Augraphy pipeline makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
+%Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
+%\begin{lstlisting}[language=Python]
+%from augraphy import *
+%pipeline = default_augraphy_pipeline()
+%img = cv2.imread("image.png")
+%data = pipeline.augment(img)
+%augmented_img = data["output"]
+%\end{lstlisting}
+
+%\subsection{Base}
+%\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself.
 The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\
 
-There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality.
+%There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality.
 Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.
 
-\subsubsection{Augmentation}
-Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
-Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.\\
+There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.
+%Two additional classes --- \texttt{OneOf} and \texttt{PaperFactory} --- provide additional variation to pipelines in ways 
+We now discuss each of these:
 
+%\subsubsection{Augmentation}
+\smallskip
+\noindent\textbf{\texttt{Augmentation}.} ~The \texttt{Augmentation} class is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
+Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.
 This class also contains a method which interacts with the probability data, dynamically generating a second floating point probability value and using this to decide whether the augmentation should be applied at runtime.
 
-\subsubsection{AugmentationResult}
-After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
+%\subsubsection{AugmentationResult}
+\smallskip
+\noindent\textbf{\texttt{AugmentationResult}.} ~After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
 These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.
 
-\subsubsection{AugmentationSequence}
-A list of \texttt{Augmentation}s -- together with the intent to apply those Augmentations in sequence -- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
-In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in .
-\texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
+%\subsubsection{AugmentationSequence}
+\smallskip
+\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
+In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
 
-\subsubsection{AugmentationPipeline}
-The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life.
+%\subsubsection{AugmentationPipeline}
+\smallskip
+\noindent\textbf{\texttt{AugmentationPipeline}.} ~The bulk of the innovation in \emph{Augraphy} resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life.
 Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
@@
 Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository.
-An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.\\
+An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.
 
@@
 Others, like a coffee spill, change properties of the paper itself.
-Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.\\
+Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.
+Effectively capturing processes like these in reproducible augmentations means separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
+ils down to the definition and application of one or more pipelines to one or more images.
 
-Effectively capturing processes like these in reproducible augmentations meant separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
-Augraphy pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
-After transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper.
-Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.\\
-
-Use of the Augraphy library to produce a dataset for model training — will be covered in some detail later — boils down to the definition and application of one or more pipelines to one or more images.\\
-
-The value added by the \texttt{AugrapyPipeline} class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
+The value added by the \texttt{AugrapyPipeline} class over a bare list of functions mapped over an image is principally in the collection of metadata:
+the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
 This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.
 
-\subsubsection{OneOf}
-Real-world processes generally allow for objects to exist in multiple states over time.
+\smallskip
+There are two additional classes that provide additional functionality in order to round out the \emph{Augraphy} library:
+
+%\subsubsection{OneOf}
+%\smallskip
+\noindent\textbf{\texttt{OneOf}.} ~Real-world processes generally allow for objects to exist in multiple states over time.
 To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.
 
-\subsubsection{PaperFactory}
-We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
+%\subsubsection{PaperFactory}
+\smallskip
+\noindent\textbf{\texttt{PaperFactory}.} ~We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
 We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline.
 This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image.
-The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the "printing" onto another "sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database.
+The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database.
 Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.
 
-\subsection{Augmentations}
-The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}.
+\smallskip
+Interoperability and flexibility are core requirements of any data augmentation library, so \emph{Augraphy} includes several utility classes designed to improve developer experience:
+
+%\smallskip
+\noindent\textbf{\texttt{ComposePipelines}.} ~This class provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.
+
+\smallskip
+\noindent\textbf{\texttt{Foreign}.} ~This class can be used to wrap augmentations from external projects like \emph{Albumentations} and \emph{imgaug}.
+
+\smallskip
+\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for simulating ``printing".
+
+%\subsection{Augmentations}
+%The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}.
 We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\
 
-Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset.
+%Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset.
 Augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
@@
 
-Figures 2 and 3 contain representative images of each augmentation applied to this very document.
+%Figures 2 and 3 contain representative images of each augmentation applied to this very document.
 Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.
@@
 
-\subsection{Utilities}\label{utilities}
-Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience.
+%\subsection{Utilities}\label{utilities}
+%Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience.
 Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively
 
-\begin{enumerate}
-\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
-\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
-\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
-\end{enumerate}
+%\begin{enumerate}
+%\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
+%\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
+%\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
+%\end{enumerate}
+\emph{Augraphy} pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
+Afterch will be covered in some detail in the next section Î transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper.
+Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.
+Use of the Augraphy library to produce a dataset for model training Î
+
 \section{Deep Learning with Augraphy}
@@
 \includegraphics[width=\textwidth]{sidebyside.png}
-\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.} \label{fig4}
+\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
 \end{figure}

### 2023-01-17 paper.tex
update intro figure with archetype

@@
 
-\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
-\centering
-\fbox{
-    \begin{minipage}{2in}
-        \hfill\vspace{1in}
-    \end{minipage}
-    }
-\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
+%\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
+%\centering
+%\fbox{
+%    \begin{minipage}{2in}
+%        \hfill\vspace{1in}
+%    \end{minipage}
+%    }
+%\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
+%\end{figure}
+
+\begin{figure}
+    \centering\scalebox{0.475}{
+    \includegraphics{figures/archetype-memo.pdf}}
+    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP.
+We re-created a clean version of (a) in (b).
+We then create a noisy version of (b) by applying several augmentations to it to produce (c).}
+    \label{fig:intro}
 \end{figure}
@@
 \emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
-\emph{Augraphy} offers \numAugraphyAugmentations~ individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
-The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~X and in Figure~Y.
+\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
+The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
 This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

### 2023-01-17 paper.tex
formatting changes for spacing

--- 2023-01-17 paper.tex
@@
 \renewcommand{\floatpagefraction}{.8}
+
+% Spacing around floats
+\setlength{\floatsep}{11pt plus 2pt minus 4pt}
+\setlength{\textfloatsep}{11pt plus 2pt minus 4pt}
+\setlength{\dblfloatsep}{\floatsep}
+\setlength{\dbltextfloatsep}{11pt plus 2pt minus 4pt}
+\setlength{\intextsep}{\floatsep}
+\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}
 
@@
 To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library.
-This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.\\
+This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
 
@@
 After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively.
-The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is "unpacking" higher-dimensional features from its low-dimensional latent representation.
+The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is ``unpacking" higher-dimensional features from its low-dimensional latent representation.
 After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier.
@@
 \subsection{Data Generation}
-Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\
+Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.
 
@@
 For the Augraphy model, we produced a dataset 10x larger, by duplicating each of the ground truth images, then running 10 Augraphy pipelines against each copy.
-Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.\\
+Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.
 
@@
 With Augraphy, we expected that we could use the BadPhotoCopy augmentation to produce the dark regions and a combination of the strikethrough behavior from the Markup augmentation and the smooth curve shading behavior of the PencilScribbles augmentation to add the last feature to the ground-truth data.
-The PaperFactory augmentation makes the paper texture overlay trivial and repeatable.
-In the end, we executed the following pipeline:
+The PaperFactory augmentation makes the paper texture overlay trivial and repeatable. In the end, we executed the following pipeline:
 
@@
 
-In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.\\
+In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.
 
@@
 \subsection{Training Regime}
-We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\
+We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.
 
 Training proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs.
-The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.\\
+The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.
 
@@
 The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features.
-Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.\\
+Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.
 
@@
 By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output.
-Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.\\
+Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.
 
@@
 \subsection{Augraphy Enhancements}
-Several upgrades to the Augraphy library itself are also planned.
+Several upgrades to the Augraphy library itself are also planned:
 
-\subsubsection{Scaling}
-While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.
+%\subsubsection{Scaling}
+\smallskip\noindent\textbf{Scaling.} ~While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.
 
-\subsubsection{Performance}
-The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware.
+%\subsubsection{Performance}
+\smallskip\noindent\textbf{Performance.} ~The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware.
 Performance enhancements to the library are already underway, which will decrease pipeline execution time dramatically, enabling faster creation of larger datasets on more common hardware.

### 2023-01-25 paper.tex
replace example augmentations figure
fold motivation into augraphy section

@@
 
-\section{Introduction and Motivation}
-%Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.
-Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths.
-However, collecting or otherwise determining a set of labels for training data is quite challenging.
-In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\
-%
-%Most often, source documents are too old, and often were created before the advent of digital storage media.
-Some documents are one-offs, produced ad-hoc in the typewriter era, but many more still were printed directly from the text editor used to write them, with no copy saved even after it became possible to do so.
-Document analysis and understanding tasks require these clean images for analysis.
-For these reasons, it's much easier to take clean documents and add distorting features to them with a tool like Augraphy than to start with the warped images and find or create ground-truths.
-
+\section{Introduction}
 The modern world provides a plethora of tasks that require the need for automated and intelligent solutions for handling unstructured data.
@@
 
-\section{Related Work}
+\section{Related Work}\label{sec:related-work}
 
@@
 
-%\section{NoisyOffice}
-%Many document-focused datasets exist, but most are designed for tasks like layout detection \cite{ref_RDCL2019}, content extraction \cite{ref_tobacco800}, or handwriting recognition \cite{ref_icdar}.
-the only publically-available dataset we could find that was exclusively focused on digitally-generated modern documents was NoisyOffice \cite{ref_NoisyOffice}.\\
+%\section{Document Distortion, Theory \& Technique}
+%Many approaches exist for adding features to an image, and many types of feature can be generated.
+The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\
 %
-%This database \cite{ref_NoisyOfficeDatabase}, hosted on the UCI Machine Learning Repository \cite{ref_UCIMLR}, was created for training image processing filters, including denoisers and superresolution models.
-NoisyOffice includes three types of image:
-%
-%\begin{enumerate}
-%\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
-%\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
-%\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
-%\end{enumerate}
-%
-%Assembling the NoisyOffice database was a great service to the document analysis community, but for our purposes, the set is too limited:
-%
-%\begin{itemize}
-%\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
-%\item the text is all English-language
-%\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
-%\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models.
-%\end{itemize}
-%
-%Rather than providing a direct answer to these, Augraphy does not generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis task while relying on users to supply the ground truth images.
-%
-%\section{DocCreator}
-%In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator \cite{ref_DocCreator} seeming to occupy that niche.\\
-%
-%DocCreator contains character-set-level distortions, a mechanism for overlaying characters onto an arbitrary paper texture akin to merge technique \#1, and also includes an experimental tool for fusing the document image onto one of several 3D meshes to simulate physical alterations to the document like a crumpled and smoothed page.\\
-%
-%While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \textit{modern} documents.
-Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in \texttt{C++}, making it unsuitable for use either in a semi-automated data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration.
-
-\section{Document Distortion, Theory \& Technique}
-Many approaches exist for adding features to an image, and many types of feature can be generated.
-The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\
-
-These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.
+%These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.
 A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
@@
 Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\
-
-Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
+%
+%Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
 Every feature just listed has either a direct implementation already within the library or on the development roadmap, with more planned.\\
-
-Some techniques exist for introducing these features into images of documents, including but not limited to the following:
-\begin{enumerate}
-\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
+%
+%Some techniques exist for introducing these features into images of documents, including but not limited to the following:
+%\begin{enumerate}
+%\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
 The NoisyOffice team did this.
-\item Similarly, any markup features may be generated and overlaid by the same methods.
-\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
-\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
-\end{enumerate}
-
-Augraphy already has a story for the first three, with the fourth in planning.
+%\item Similarly, any markup features may be generated and overlaid by the same methods.
+%\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
+%\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
+%\end{enumerate}
+%
+%Augraphy already has a story for the first three, with the fourth in planning.
 
@@
 This section dives into detail about the \emph{Augraphy} library.
-We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
+We first provide a high-level motivation for and overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
+
+\subsection{Motivation}
+
+As mentioned in Section~\ref{sec:related-work}, several libraries and tools exist for augmenting image data.
+These approaches alter images by adding Gaussian noise, applying blurring filters, and using geometric transformations like scaling, rotating, translating, cropping, downsampling, and so on.
+While these types of modifications are useful in general image applications, they bear little relation to the types of features comonly found in real-world document image datasets.
+
+A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
+These are cut to size and stacked, then bound in reams and sent out for sale and use.
+This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream.
+At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink.
+Any of these processes may alter the local texture or global topology of the sheet.
+The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to many other operations.
+\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
 

### 2023-01-25 paper.tex

--- 2023-01-20 paper.tex
@@
 \usepackage{times}
+\usepackage{wrapfig}
 \renewcommand{\floatpagefraction}{.8}
@@
 
+\subsection{Face Detection Robustness Testing}
+
+In this section, we use \emph{Augraphy} to investigate the robustness of face detection models on images that have been altered by \emph{Augraphy}.
+In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers, which are often scanned from the physical world by noisy scanners.
+Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
+
+\begin{wraptable}{r}{5cm}
+    \centering
+    \caption{Face detection performance.}
+    \begin{tabular}{lr}
+    \toprule
+        \textbf{Model} & \textbf{Accuracy} \\
+        \midrule
+        Azure & 57.1\%\\
+        Google & 60.1\%  \\
+        Amazon & 49.1\% \\
+        UltraFace & 4.5\%\\
+        \bottomrule
+    \end{tabular}
+    \label{tab:face-detection-results}
+\end{wraptable}
+
+We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}.
+Then, we use \emph{Augraphy} to generate 10 altered versions of each image and manually remove any augmented image where the face(s) is not reasonably visible.
+We then test four face detection models on the noisy and noise-free images.
+These models are: proprietary face detection models from Google,\footnote{\url{https://cloud.google.com/vision/docs/detecting-faces}} Amazon,\footnote{\url{https://aws.amazon.com/rekognition/}} and Microsoft\footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services/face}}, and lastly the freely-available UltraFace\footnote{\url{https://github.com/onnx/models/tree/main/vision/body_analysis/ultraface}} model.
+%We then test Microsoft Azure's face detection model on the noise-free and noisy images.
+
+Table~\ref{tab:face-detection-results} shows face detection accuracy of both models on the noisy test set, and example images where no faces were detected by the Microsoft model are shown in Figure \ref{fig:face-detection-mistakes}.
+We see that all four models struggle on the \emph{Augraphy}-augmented data, with the proprietary models seeing detection performances drop to between roughly 50-60\%, and UltraFace detecting only 4.5\% of faces that it found in the noise-free data.
+
+\begin{figure}
+    \centering\scalebox{0.47}{
+    \includegraphics{figures/azure_1x3_face_errors.pdf}}
+    \caption{Example augmented images that yielded false-positive predictions with the Azure face detector.}
+    \label{fig:face-detection-mistakes}
+\end{figure}
+
 \section{Future Work}

### 2023-01-30 paper.tex
add number of augmentations, augmentation-matrix image

@@
 
-\newcommand{\numAugraphyAugmentations}{\emph{n}}
+\newcommand{\numAugraphyAugmentations}{\emph{26}}
 
@@
 Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
+We discuss the Augraphy tool, showing how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document de-noising, as well as generating challenging test data for evaluating model robustness on document image modeling tasks.
 
@@
 \section{Introduction}
-The modern world provides a plethora of tasks that require the need for automated and intelligent solutions for handling unstructured data.
-Often, this data is in the form of documents, and these documents may appear noisy, especially if they have been captured from the physical world via printing, scanning, or photocopying processes.
-Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human annotations like highlighting or pencil marks can add noise to the page.
+Life in the modern world involves a plethora of tasks that require automated and intelligent solutions for handling unstructured data.
+Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been altered in the physical world by printing, scanning, or photocopying processes.
+Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.
 
-Many tasks involving machine learning are impacted by document noise.
-High-level tasks like document classification and information extraction must often be able to perform on noisily scanned document images.
+Many machine learning operations involving documents are impacted by the presence of noise; high-level tasks like document classification and information extraction are often expected to perform well even on noisily-scanned document images.
 For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
@@
     \centering
-    \caption{Comparison of various image-based data augmentation libraries.}
+    \caption{Comparison of various image-based data augmentation libraries.
+Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities.
+Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
     \scalebox{0.9}{
@@
     \midrule
-        \emph{Augmentor} \cite{augmentor} & & \xmark &  & \cmark & MIT \\ 
-        \emph{Albumentations} \cite{ref_albumentations} &  & \xmark & \cmark & \cmark & MIT \\
-        \emph{imgaug} \cite{ref_imgaug} & & \xmark & \cmark & \cmark & MIT \\
-        \emph{Augly} \cite{Papakipos2022-gq-augly} & & \xmark & & \cmark & MIT \\
-        \emph{Pytorch} \cite{pytorch} & & \xmark & \cmark & \cmark & BSD-style \\
-        \emph{DocCreator} \cite{ref_DocCreator} & & \cmark & \xmark & \xmark & LGPL-3.0 \\
+        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
+        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
+        \emph{imgaug} \cite{ref_imgaug} & 168& \xmark & \cmark & \cmark & MIT \\
+        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
+        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
         \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
@@
 \scalebox{0.33}{
-\includegraphics[]{pipeline.png}}
+\includegraphics[]{figures/pipeline.png}}
 \caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
@@
 Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
-These augmentations are listed in Table~\ref{tab:augmentations}.
+These augmentations are listed in Table~\ref{tab:augmentations}, and examples are shown in Figure~\ref{fig:augraphy-examples-github}.
 As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{augmentations1.png}
-\caption{Examples of each augmentation.} \label{fig2}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=\textwidth]{augmentations1.png}
+%\caption{Examples of each augmentation.} \label{fig2}
+%\end{figure}
+%
+%\begin{figure}
+%\includegraphics[width=\textwidth]{augmentations2.png}
+%\caption{Examples of each augmentation.} \label{fig3}
+%\end{figure}
 
 \begin{figure}
-\includegraphics[width=\textwidth]{augmentations2.png}
-\caption{Examples of each augmentation.} \label{fig3}
+    \centering\scalebox{0.34}{
+    \includegraphics{figures/augraphy_examples_github.png}}
+    \caption{A subset of various \emph{Augraphy} augmentations on sample images.}
+    \label{fig:augraphy-examples-github}
 \end{figure}
@@
 \subsection{Model Architecture}
-To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library.
+To evaluate Augraphy, we trained an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}.
 This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
-
-This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step.
-After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively.
-The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is ``unpacking" higher-dimensional features from its low-dimensional latent representation.
-After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier.
-Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions.
-This final convolution uses the sigmoid function as its activation function.
-All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.
 
@@
 \begin{figure}\label{fig4}
-\includegraphics[width=\textwidth]{sidebyside.png}
+\includegraphics[width=\textwidth]{figures/sidebyside.png}
 \caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}

### 2023-02-04 paper.tex
various changes

@@
 \usepackage{times}
-\usepackage{wrapfig}
 \renewcommand{\floatpagefraction}{.8}
+\usepackage{etoolbox}
+\AtBeginEnvironment{quote}{\par\singlespacing\small}
 
@@
 \newcommand{\numAugraphyAugmentations}{\emph{26}}
+\newcommand{\numNoisyOfficeUNetEpochs}{\emph{426}}
+\newcommand{\ocrCleanLevenshteinDistance}{\emph{TODO}}
+\newcommand{\ocrAugraphyAverageLevenshteinDistance}{\emph{TODO}}
 
@@
 \begin{abstract}
-This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
-Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-We discuss the Augraphy tool, showing how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document de-noising, as well as generating challenging test data for evaluating model robustness on document image modeling tasks.
+This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing distortions commonly seen in real-world document image datasets.
+Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
+This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
 
@@
 
-\section{Introduction}
-Life in the modern world involves a plethora of tasks that require automated and intelligent solutions for handling unstructured data.
-Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been altered in the physical world by printing, scanning, or photocopying processes.
+\section{Introduction and Motivation}
+Daily life in the modern world involves a plethora of tasks requiring the handling of unstructured data.
+Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been physically altered by printing, scanning, or photocopying processes.
 Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.
 
-Many machine learning operations involving documents are impacted by the presence of noise; high-level tasks like document classification and information extraction are often expected to perform well even on noisily-scanned document images.
+Many machine learning operations involving documents are impacted by the presence of noise, while high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
 For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
 Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
-Further, the lower-level task of document de-noising tackles the document noise problem more directly by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
-Such tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.
-
-%\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
-%\centering
-%\fbox{
-%    \begin{minipage}{2in}
-%        \hfill\vspace{1in}
-%    \end{minipage}
-%    }
-%\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
-%\end{figure}
+The lower-level task of document de-noising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
+All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.
 
@@
 
-For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office room procedures.
+For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office procedures.
 \emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
-\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
+\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
 The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
@@
         \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
-        \emph{imgaug} \cite{ref_imgaug} & 168& \xmark & \cmark & \cmark & MIT \\
+        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
         \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
@@
 
-\section{Related Work}\label{sec:related-work}
+\section{Related Work}
 
-%This section discusses prior work related to document data augmentation, robustness testing, and document de-noising.
 This section discusses prior work related to data augmentation and robustness testing, especially as it relates to document understanding and processing tasks.
@@
 \subsection{Data Augmentation}
-A wide variety of data augmentation tools and pipelines exist for machine learning tasks ranging from natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
-In the image realm of image processing and computer vision, data augmentation tools and pipelines include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, Pytorch \cite{pytorch}, and \emph{imgaug} \cite{ref_imgaug}.
-Augmentation strategies from these image-centric libraries are typically general purpose, and include image transformations like rotations, warps, and color modifications.
-Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image-based data augmentation libraries and tools.
+A wide variety of data augmentation tools and pipelines exist for machine learning tasks, including  natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
+In the latter realm, popular tools include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, and \emph{imgaug} \cite{ref_imgaug}.
+Augmentation strategies from these image-centric libraries are typically general-purpose, and include transformations like rotations, warps, and color modifications.
+Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools.
 As can be seen, these other data augmentation libraries do not specifically provide support for imitating the corruptions commonly seen in document analysis corpora.
@@
 A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
-\emph{DocCreator} differs from \emph{Augraphy} in several ways, however.
-The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is meant to replicate noise caused by noisy office room procedures.
-\emph{DocCreator} is also written in the C++ programming language and is a monolithic what-you-see-is-what-you-get (WYSIWYG) tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
-\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, and can easily be used alongside other Python packages.
+\emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
+The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate noise caused by office room procedures.
+\emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
+\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_PyTorch}.
 
@@
 More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
-Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications.
+Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications to produce human-readable distortions which challenge OCR models.
 
-%\section{Document Distortion, Theory \& Technique}
-%Many approaches exist for adding features to an image, and many types of feature can be generated.
+\section{Document Distortion, Theory \& Technique}
+Many approaches exist for adding features to an image, and many types of feature can be generated.
 The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\
-%
-%These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.
+
+These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.
+
 A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
@@
 Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\
-%
-%Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
-Every feature just listed has either a direct implementation already within the library or on the development roadmap, with more planned.\\
-%
-%Some techniques exist for introducing these features into images of documents, including but not limited to the following:
-%\begin{enumerate}
-%\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
+
+Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
+Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.\\
+
+Some techniques exist for introducing these features into images of documents, including but not limited to the following:
+\begin{enumerate}
+\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
 The NoisyOffice team did this.
-%\item Similarly, any markup features may be generated and overlaid by the same methods.
-%\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
-%\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
-%\end{enumerate}
-%
-%Augraphy already has a story for the first three, with the fourth in planning.
+\item Similarly, any markup features may be generated and overlaid by the same methods.
+\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
+\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
+\end{enumerate}
+
+Augraphy already has a story for the first three, with the fourth in planning.
 
@@
 This section dives into detail about the \emph{Augraphy} library.
-We first provide a high-level motivation for and overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
-
-\subsection{Motivation}
-
-As mentioned in Section~\ref{sec:related-work}, several libraries and tools exist for augmenting image data.
-These approaches alter images by adding Gaussian noise, applying blurring filters, and using geometric transformations like scaling, rotating, translating, cropping, downsampling, and so on.
-While these types of modifications are useful in general image applications, they bear little relation to the types of features comonly found in real-world document image datasets.
-
-A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
-These are cut to size and stacked, then bound in reams and sent out for sale and use.
-This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream.
-At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink.
-Any of these processes may alter the local texture or global topology of the sheet.
-The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to many other operations.
-\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
+We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
 
@@
 \emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}.
-\emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments.
+\emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3.
 Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
-%Examples of output generated by \emph{Augraphy} are shown in Figure~\ref{fig:augraphy_examples_3x5}.
 
@@
 data = pipeline.augment(img)
-augmented = data["output"]
+augmented_img = data["output"]
 \end{lstlisting}
 Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
-%We wanted the library
-The library is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
+
+\emph{Augraphy} is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
 The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
 
-%We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\
+\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
+Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
+\begin{figure}
+\centering
+\scalebox{0.33}{
+\includegraphics[]{figures/pipeline.png}}
+\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
+\end{figure}
 
-\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into a pipeline object that carries out the image manipulation.
-Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
 \emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
@@
 
-\begin{figure}
-\centering
-\scalebox{0.33}{
-\includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
-\end{figure}
-
 \subsection{Augraphy Augmentations}
@@
 Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
-These augmentations are listed in Table~\ref{tab:augmentations}, and examples are shown in Figure~\ref{fig:augraphy-examples-github}.
+These augmentations are listed in Table~\ref{tab:augmentations}.
 As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
@@
 Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
-These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates a book binding effect with shadow and curved lines to imitate how a page from a book might appear after being scanned with a flatbed scanner.
-Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations as well.
-Descriptions of- and motivation for each augmentation are available on GitHub. \footnote{\url{https://github.com/sparkfish/augraphy}}
-% TODO: is there a more precise link for these descriptions?
+These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates an effect with shadow and curved lines to imitate how a page from a book might appear after capture by a flatbed scanner.
 
-%Augraphy is designed to replicate noise-like effects seen in real-world documents, and the library's
-%, so each augmentation represents a feature that will appear in the final dataset.
-%augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
-%Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well.
-The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\
+Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations for completeness and utility.
+Descriptions of each augmentation are available online, along with the motivation for their development. \footnote{\url{https://augraphy.readthedocs.io/en/latest/}}
 
-% TODO: I don't think this table is entirely correct, some augmentations might be listed in the wrong columns
 \begin{table}[]
     \centering
-    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase.}
+    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within the pipeline.
+Augmentations that work well in more than one phase are listed in the last column.}
     \scalebox{0.81}{
-    \begin{tabular}{lll}
+    \begin{tabular}{llll}
     \toprule
-        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} \\
+        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
         \midrule
-        \textsf{BleedThrough} & \textsf{BrightnessTexturize} & \textsf{BadPhotoCopy} \\
-        \textsf{DirtyDrum} & \textsf{ColorPaper} & \textsf{BindingsAndFasteners} \\
-        \textsf{DirtyRollers} & \textsf{Gamma} & \textsf{BookBinding} \\
-        \textsf{Dithering} & \textsf{Geometric} & \textsf{Folding} \\
-        \textsf{Faxify} & \textsf{LightingGradient} & \textsf{JPEG} \\
-        \textsf{InkBleed} & \textsf{PageBorder} & \textsf{NoiseTexturize} \\
-        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{Watermark} \\
-        \textsf{LowInkLine} & & \\
-        \textsf{Markup} & & \\
-        \textsf{PencilScribbles} & & \\
+        \textsf{BleedThrough} &  \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
+        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
+        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
+        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
+        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
+        & & \textsf{Markup} & \textsf{NoiseTexturize}\\
+        & & \textsf{Faxify} & \textsf{PencilScribbles}\\
+        & & \textsf{PageBorder} & \\
         \bottomrule
@@
 \subsection{The Augraphy Library}
-\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners,
-%The library was developed in Python, to allow maximal accessibility for practitioners,
-and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
-When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented document images.
-
-%Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
-%We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
-%The default Augraphy pipeline makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
-%Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
-%\begin{lstlisting}[language=Python]
-%from augraphy import *
-%pipeline = default_augraphy_pipeline()
-%img = cv2.imread("image.png")
-%data = pipeline.augment(img)
-%augmented_img = data["output"]
-%\end{lstlisting}
-
-%\subsection{Base}
-%\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself.
-The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\
-
-%There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality.
-Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.
+\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners, and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
+When composed, augmentations from the library interact to produce complex document image transformations, generating realistic new synthetically-augmented document images.
 
 There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.
-%Two additional classes --- \texttt{OneOf} and \texttt{PaperFactory} --- provide additional variation to pipelines in ways 
+
 We now discuss each of these:
 
-%\subsubsection{Augmentation}
 \smallskip
 \noindent\textbf{\texttt{Augmentation}.} ~The \texttt{Augmentation} class is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
-Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.
-This class also contains a method which interacts with the probability data, dynamically generating a second floating point probability value and using this to decide whether the augmentation should be applied at runtime.
+Every augmentation contained in a pipeline has its own chance of being applied during that pipeline's execution.
 
-%\subsubsection{AugmentationResult}
 \smallskip
 \noindent\textbf{\texttt{AugmentationResult}.} ~After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
-These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.
+These objects also record a full copy of the augmentation runtime data, as well as any metadata that might be relevant for debugging or other advanced use.
 
-%\subsubsection{AugmentationSequence}
 \smallskip
@@
 
-%\subsubsection{AugmentationPipeline}
 \smallskip
-\noindent\textbf{\texttt{AugmentationPipeline}.} ~The bulk of the innovation in \emph{Augraphy} resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life.
-Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
+\noindent\textbf{\texttt{AugmentationPipeline}.} ~The bulk of the heavy lifting in \emph{Augraphy} resides in the Augmentation pipeline, which is our abstraction over one or more events in a physical document's life.
+
+Consider the following sequence of events:
+\begin{quote}
+The initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
 Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts.
 Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository.
+\end{quote}
 An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.
@@
 Effectively capturing processes like these in reproducible augmentations means separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
-ils down to the definition and application of one or more pipelines to one or more images.
+Producing realistically noisy document images can now be reduced to the definition and application of one or more Augraphy pipelines to some clean document images.
 
-The value added by the \texttt{AugrapyPipeline} class over a bare list of functions mapped over an image is principally in the collection of metadata:
+The value added by the \texttt{AugraphyPipeline} class over a bare list of functions mapped over an image is principally in the collection of runtime metadata:
 the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
-This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.
+This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure 1 \ref{fig:intro}.
 
 \smallskip
-There are two additional classes that provide additional functionality in order to round out the \emph{Augraphy} library:
+There are two additional classes that provide additional functionality in order to round out the \emph{Augraphy} base library:
 
-%\subsubsection{OneOf}
-%\smallskip
-\noindent\textbf{\texttt{OneOf}.} ~Real-world processes generally allow for objects to exist in multiple states over time.
-To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.
+\noindent\textbf{\texttt{OneOf}.} ~To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from the given list, and uses this to modify the image.
 
-%\subsubsection{PaperFactory}
 \smallskip
@@
 The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database.
-Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.
+Taken together, \texttt{PaperFactory} makes it trivial to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.
 
@@
 
-%\subsection{Augmentations}
-%The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}.
-We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\
-
-%Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset.
-Augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
-Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well.
-The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\
-
-%Figures 2 and 3 contain representative images of each augmentation applied to this very document.
-Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.
-
-%\begin{figure}
-%\includegraphics[width=\textwidth]{augmentations1.png}
-%\caption{Examples of each augmentation.} \label{fig2}
-%\end{figure}
-%
-%\begin{figure}
-%\includegraphics[width=\textwidth]{augmentations2.png}
-%\caption{Examples of each augmentation.} \label{fig3}
-%\end{figure}
-
 \begin{figure}
-    \centering\scalebox{0.34}{
-    \includegraphics{figures/augraphy_examples_github.png}}
-    \caption{A subset of various \emph{Augraphy} augmentations on sample images.}
-    \label{fig:augraphy-examples-github}
+\includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
+\caption{Examples of some Augraphy augmentations.} \label{fig2}
 \end{figure}
 
-%\subsection{Utilities}\label{utilities}
-%Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience.
-Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively
+\emph{Augraphy} pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
 
-%\begin{enumerate}
-%\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
-%\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
-%\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
-%\end{enumerate}
-\emph{Augraphy} pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
-Afterch will be covered in some detail in the next section Î transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper.
-Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.
-Use of the Augraphy library to produce a dataset for model training Î
+After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
+After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
+Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
+Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
 
@@
 This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data.
-We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for Augraphy analysis.
+We perform the same experiment twice, with different model designs.
+We continue to return to the NoisyOffice database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for analyzing Augraphy.
 
 \subsection{Model Architecture}
-To evaluate Augraphy, we trained an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}.
-This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
+To evaluate Augraphy, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}.
+We selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
+The second model is an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.
 
@@
 
-The PaperFactory augmentation reads and randomly crops image textures from a local directory; to this we added two \footnote{\url{https://p2.piqsels.com/preview/642/889/110/paper-crease-creased-texture.jpg
-}}, \footnote{\url{https://blog.miklavcic.si/wp-content/uploads/2011/11/white_paper_1.png}} public domain images of wrinkled paper found on Bing.
+The PaperFactory augmentation reads and randomly crops image textures from a local directory; to this we added two \footnote{\url{https://p2.piqsels.com/preview/642/889/110/paper-crease-creased-texture.jpg}}, \footnote{\url{https://blog.miklavcic.si/wp-content/uploads/2011/11/white_paper_1.png}} public domain images of wrinkled paper found with Bing.
 
 \subsection{Training Regime}
-We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.
+We fit the models described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.
 
-Training proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs.
-The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.
+Training of the UNets proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs.
+The NoisyOffice model finished training after \numNoisyOfficeUNetEpochs epochs, while the Augraphy model trained for the full 600 epochs.
 
@@
 
+The NAFNet instances trained for 100 epochs, using the default settings provided from the GitHub version.
+All code used in these experiments is available in the Augraphy-Paper GitHub \footnote{\url{https://github.com/sparkfish/augraphy-paper}}.
+
 \subsection{Results}
-Sample predictions from each model on the validation task are presented in Figure 1.
-As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue.
-The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features.
-Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.
+Sample predictions from each model on the validation task are presented in Table 1.
+A new dataset, ShabbyPagesReal, was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
+ShabbyPagesReal is fully out-of-distribution for the models in our experiments, and has a much higher degree of diversity than the NoisyOffice set, providing good conditions for evaluating Augraphy's effect.
+As expected, the NoisyOffice models perform admirably, fitting extremely well to the low-diversity data of the NoisyOffice set, but they do struggle to fully remove the coffee stain feature, leaving some residue.
+The SSIM score indicates that the Augraphy models generalize much better, though they do overcompensate for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.
+
+%[TODO: is this true?] The Augraphy models clearly outperform the NoisyOffice models at stain removal, but do not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features.
 
@@
 \caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
-\end{figure}
+\end{figure} %[TODO: can we show this a better way?]
 
@@
 \caption{Model training statistics and performance on NoisyOffice validation task}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
+\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
 \hline
-Metric & NoisyOffice & Augraphy\\
+Metric & PSNR & SSIM & RMSE\\
 \hline
-PSNR & 63.09152246942623 & 63.3491691640664\\
-SSIM & 0.8726093605602885 & 0.8662918306486613\\
-RMSE & 0.1878745854176291 & 0.18310202817380003\\
-Test Loss & 0.0011 & 0.0012\\
-Test MAE & 0.0150 & 0.0129\\
-Validation Loss & 7.5551e-04 & 8.22202e-04\\
-Validation MAE & 0.01236 & 0.01076\\
-Training Time & 190ms/step & 218ms/step\\
+NoisyOffice\_UNet & 63.09 & 0.87 & 0.19\\
+Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
+NoisyOffice\_NAFNet & & &
+Augraphy\_NAFNet & & &
 \hline
@@
 
-\subsection{Face Detection Robustness Testing}
+\section{Robustness Testing}
+We use Augraphy to add noise to an image of text with known groundtruth.
+The Tesseract \cite{ref_tesseract} pre-trained OCR model's performance on the clean image is compared to the OCR result on the Augraphy-noised image, then to the true groundtruth string, using the Levenshtein distance.
+These measures are averaged over 1000 trials, with different Augraphy effects, to give some indication of Augraphy's effect on producing human-readable document images for challenging OCR tasks.
 
-In this section, we use \emph{Augraphy} to investigate the robustness of face detection models on images that have been altered by \emph{Augraphy}.
-In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers, which are often scanned from the physical world by noisy scanners.
-Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
+%% [TODO: render this]
+%% \begin{figure}
+%% \includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
+%% \caption{Groundtruth image (left), sample of Augraphy output (right).} \label{fig5}
+%% \end{figure}
 
-\begin{wraptable}{r}{5cm}
-    \centering
-    \caption{Face detection performance.}
-    \begin{tabular}{lr}
-    \toprule
-        \textbf{Model} & \textbf{Accuracy} \\
-        \midrule
-        Azure & 57.1\%\\
-        Google & 60.1\%  \\
-        Amazon & 49.1\% \\
-        UltraFace & 4.5\%\\
-        \bottomrule
-    \end{tabular}
-    \label{tab:face-detection-results}
-\end{wraptable}
+%% [TODO: get results]
+%% \begin{table}[]
+%%     \centering
+%%     \caption{Measuring \emph{Augraphy}'s effect on OCR model performance.}
+%%     \scalebox{0.81}{
+%%     \begin{tabular}{lll}
+%%     \toprule
+%%     \textbf{Groundtruth String} & \textbf{OCR output on clean image \\ distance to true string} & \textbf{Average OCR output on Augraphy-noised images \\ distance to true string} \\
+%%     \midrule
+%%     "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum." & \ocrCleanLevenshteinDistance & \ocrAugraphyAverageLevenshteinDistance
+%%     \bottomrule
+%%     \end{tabular}}
+%%     \label{tab:levenshtein}
+%% \end{table}
 
-We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}.
-Then, we use \emph{Augraphy} to generate 10 altered versions of each image and manually remove any augmented image where the face(s) is not reasonably visible.
-We then test four face detection models on the noisy and noise-free images.
-These models are: proprietary face detection models from Google,\footnote{\url{https://cloud.google.com/vision/docs/detecting-faces}} Amazon,\footnote{\url{https://aws.amazon.com/rekognition/}} and Microsoft\footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services/face}}, and lastly the freely-available UltraFace\footnote{\url{https://github.com/onnx/models/tree/main/vision/body_analysis/ultraface}} model.
-%We then test Microsoft Azure's face detection model on the noise-free and noisy images.
-
-Table~\ref{tab:face-detection-results} shows face detection accuracy of both models on the noisy test set, and example images where no faces were detected by the Microsoft model are shown in Figure \ref{fig:face-detection-mistakes}.
-We see that all four models struggle on the \emph{Augraphy}-augmented data, with the proprietary models seeing detection performances drop to between roughly 50-60\%, and UltraFace detecting only 4.5\% of faces that it found in the noise-free data.
-
-\begin{figure}
-    \centering\scalebox{0.47}{
-    \includegraphics{figures/azure_1x3_face_errors.pdf}}
-    \caption{Example augmented images that yielded false-positive predictions with the Azure face detector.}
-    \label{fig:face-detection-mistakes}
-\end{figure}
+%% In Table 3 \ref{tab:levenshtein}, it can be seen that Augraphy introduces features which confound the Tesseract pre-trained OCR model.
 
@@
 Two other players in the same space were examined and found lacking for our purposes, motivating the creation of this library.
-We described creating an Augraphy-noised version of the NoisyOffice dataset, then compared some preliminary results obtained by training a convolutional U-Net on these datasets.
+We described creating an Augraphy-noised version of the NoisyOffice dataset, then compared some preliminary results obtained by training a convolutional U-Net and a NAFNet on these datasets.
 Finally, we discussed some future directions for research, and the continued evolution of this tool.

### 2023-02-05 paper.tex
Minor formatting update on table widths
Removed numbers from abstract

@@
 Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.
+This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and generating challenging test data for evaluating model robustness on document image modeling tasks.
 
@@
 Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
-The lower-level task of document de-noising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
+The lower-level task of document denoising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
 All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.
@@
 \begin{figure}
-    \centering\scalebox{0.475}{
+    \centering
+
+    \resizebox{\textwidth}{!}{
     \includegraphics{figures/archetype-memo.pdf}}
+
     \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP.
@@
 We then create a noisy version of (b) by applying several augmentations to it to produce (c).}
+
     \label{fig:intro}
@@
 Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
-    \scalebox{0.9}{
+    \resizebox{0.9\textwidth}{!}{
     \begin{tabular}{lccccc}
     \toprule
-        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
-        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
+         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
+        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
     \midrule
@@
 Augmentations that work well in more than one phase are listed in the last column.}
-    \scalebox{0.81}{
+    \resizebox{0.9\textwidth}{!}{
     \begin{tabular}{llll}

### 2023-02-05 paper.tex
Fixed PyTorch reference

@@
 \emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
-\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_PyTorch}.
+\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_pytorch}.
 

### 2023-02-05 paper.tex
Fixed NumPy citation reference

@@
 \end{center}
-\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}.
+\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{ref_numpy}.
 \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3.

### 2023-02-05 paper.tex
Adjusted section 4.1 to better fit on 1 page

--- 2023-02-05 paper.tex
@@
 \definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\definecolor{superlightgray}{RGB}{242,242,242}
 
@@
 \emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
-It is registered on the Python Package Index (PyPI) and can be installed using
-\begin{center}
-\textbf{\texttt{pip install augraphy}}
-\end{center}
-\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}.
-\emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3.
-Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
+It is registered on the Python Package Index (PyPI) and can be installed simply using \colorbox{superlightgray}{\textbf{\texttt{pip install augraphy}}}.
 
-\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Transforming an image with \emph{Augraphy}.}]
+\emph{Augraphy} requires only a few commonly-used Python scientific computing or image handling packages, such as NumPy \cite{ref_numpy}, and has been tested on Windows, Linux, and Mac computing environments and supports recent major versions of Python 3.
+Below is a basic out-of-the-box \emph{Augraphy} pipeline demonstrating its usage:
+
+\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Augmenting a document image with \emph{Augraphy}.}]
 import augraphy; import cv2
@@
 \end{lstlisting}
+
 Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
@@
 Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
+
 \begin{figure}
 \centering
-\scalebox{0.33}{
+\scalebox{0.3}{
 \includegraphics[]{figures/pipeline.png}}
@@
 
-The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator is utilized for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
-After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
+The paper phase applies transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
+After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
 After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
-Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
+Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
 Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
@@
 \smallskip
-There are two additional classes that provide additional functionality in order to round out the \emph{Augraphy} base library:
+There are also two classes that provide additional functionality in order to round out the \emph{Augraphy} base library:
 

### 2023-02-05 paper.tex
Cleaned up Figure 1 and added labels to improve readability
Added caption to test data generation pipeline

@@
 \usepackage{etoolbox}
+\usepackage{multirow}
+\usepackage{tabularx}
 \AtBeginEnvironment{quote}{\par\singlespacing\small}
@@
 
+    \begin{tabularx}{\linewidth}{*{3}{>{\centering\arraybackslash}X}}
+        Noisy Original & Clean Reproduction & Augraphy Reproduction \\
+        \multicolumn{3}{c}{
             \resizebox{\textwidth}{!}{
-    \includegraphics{figures/archetype-memo.pdf}}
+                \includegraphics{figures/archetype-memo.pdf}}}      \\
+        (a) & (b) & (c) \\
+    \end{tabularx}
 
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[language=Python, label={lst:test-pipeline}, caption={Pipeline used for test data generation.}]
 ink_phase = []
@@
 ]
-
 AugraphyPipeline(ink_phase, paper_phase, post_phase)

### 2023-02-05 paper.tex
Added NAFNet reference citation

@@
 We selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
-The second model is an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.
+The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.
 

### 2023-02-05 paper.tex
Streamlined future work and conclusions section

@@
 
-\section{Future Work}
-This section describes new directions for research and development.
+\section{Conclusion and Future Work}
+We presented Augraphy, a framework for generating realistic synthetically-augmented datasets of document images.
+Other available image augmentation tools were examined and found to lack features needed for our purposes, motivating the creation of this library specifically targeting the types of alterations and degradations seen in document images.
 
-\subsection{Tuning the Pipeline}
-The pipeline used to generate training data for the Augraphy model was extremely naive, and only contained four augmentations, most with default parameters, demonstrating Augraphy's high degree of both utility and ease-of-use.
-However, much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from.
-Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters to generate training images closer to the validation set.
+We also described the process for creating new document image datasets that contain synthetic real-world noise using Augraphy, then compared results obtained by training a convolutional U-Net and a NAFNet on these datasets.
 
-\subsection{Additional Techniques}
-For brevity, this article only includes experimental results for one type of model.
-We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion and generative adversarial networks, and ensembles of these.
-During the validation task, the naive Augraphy model correctly removed the page fold and wrinkle noise, but visually degraded regions of the foreground text.
-By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output.
-Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.
+Future work on the Augraphy library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on more common hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions and responding to community-initiated feature requests.
 
-\subsection{An Augraphy Dataset}
-Privacy and security concerns typically preclude the assembly of large sets of modern document images: most documents are not intended for general viewing.
-The authors have searched frequently, for over a year, and have been unable to find decently-sized (>10 images) sets of modern document images, besides the NoisyOffice set.
-We intend to release an Augraphy-generated dataset in the coming months.
-
-\subsection{Augraphy Enhancements}
-Several upgrades to the Augraphy library itself are also planned:
-
-%\subsubsection{Scaling}
-\smallskip\noindent\textbf{Scaling.} ~While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.
-
-%\subsubsection{Performance}
-\smallskip\noindent\textbf{Performance.} ~The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware.
-Performance enhancements to the library are already underway, which will decrease pipeline execution time dramatically, enabling faster creation of larger datasets on more common hardware.
-
-\section{Conclusion}
-We presented Augraphy, an augmentation framework for generating realistic datasets of modern document images.
-Two other players in the same space were examined and found lacking for our purposes, motivating the creation of this library.
-We described creating an Augraphy-noised version of the NoisyOffice dataset, then compared some preliminary results obtained by training a convolutional U-Net and a NAFNet on these datasets.
-Finally, we discussed some future directions for research, and the continued evolution of this tool.
-Augraphy is licensed under the MIT open source license, and readers are invited to participate in its development on GitHub.
+Augraphy is licensed under the MIT open source license, and readers are invited to share feedback and participate in its development on GitHub.
 

### 2023-02-06 paper.tex
add OCR robustness section from old paper

@@
 
+We use the widely-used open-source Tesseract 2 engine and first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known.
+We then used Tesseract to generate OCR predictions on these noise-free documents, as a baseline for comparison.
+We considered these OCR predictions as the ground-truth labels for each document.
+Next, we generated noisy versions of the 15 documents by running them through an Augraphy pipeline, and again used Tesseract to generate OCR predictions on these noisy documents.
+We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%.
+This example use-case demonstrates the effectiveness of using Augraphy to create challenging test data for evaluating OCR systems.
+
 %% [TODO: render this]

### 2023-02-07 paper.tex

@@
 The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
+
+\emph{Augraphy} has been used in several research efforts: Larson et al.
+(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} for generating noisy document images for training a GAN for document deniosing; and Kim et al.
+2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
+
 This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

### 2023-02-09 paper.tex
substantial narrative changes, added TODOs for remaining work

--- 2023-02-06 paper.tex
@@
 \begin{abstract}
-This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing distortions commonly seen in real-world document image datasets.
+This paper introduces Augraphy, a Python library for constructing data augmentation pipelines which produce distortions commonly seen in real-world document image datasets.
 Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and generating challenging test data for evaluating model robustness on document image modeling tasks.
+This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and also for generating challenging test data to evaluate model robustness on document image modeling tasks.
 
@@
 \section{Introduction and Motivation}
-Daily life in the modern world involves a plethora of tasks requiring the handling of unstructured data.
-Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been physically altered by printing, scanning, or photocopying processes.
-Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.
+Daily life in the modern world is increasingly data-driven, involving myriad tasks which require the generation and handling of unstructured data.
+Increasingly, this data occurs in the form of messages or images, often with complex contents.
+In the office space, most data is created and stored document-form, easy to print and distribute.
+The lifetime of these documents typically includes physical alterations by printing, scanning, or photocopying operations, so real documents may appear visually very different from their original born-digital counterparts.
+Real-world processes can introduce many types of distortions: folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; human-made annotations like highlighting or pencil marks can add noise to the page.
 
-Many machine learning operations involving documents are impacted by the presence of noise, while high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
+The outcomes of many machine learning operations involving documents are impacted by the presence of such noise; high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
 For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
@@
 The lower-level task of document denoising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
-All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.
+All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation, reducing the need for human toil.
 
@@
 \emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
-The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
+The resulting images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
+
+\emph{Augraphy} has been used in several research efforts: Larson et al.
+(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document deniosing GAN; and Kim et al.
+2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
+
 This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.
@@
 \item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
-The NoisyOffice team did this.
 \item Similarly, any markup features may be generated and overlaid by the same methods.
@@
 \includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
+\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background}
+\label{fig:pipeline}
 \end{figure}
@@
 After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
+
+After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
 Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
@@
 
-Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
-These augmentations are listed in Table~\ref{tab:augmentations}.
+Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations, listed in Table~\ref{tab:augmentations}.
 As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
@@
 Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
-These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates an effect with shadow and curved lines to imitate how a page from a book might appear after capture by a flatbed scanner.
-
-Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations for completeness and utility.
-Descriptions of each augmentation are available online, along with the motivation for their development. \footnote{\url{https://augraphy.readthedocs.io/en/latest/}}
+Here we find \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates an effect with shadow and curved lines to imitate how a page from a book might appear after capture by a flatbed scanner.
 
@@
 
-\subsection{The Augraphy Library}
+Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} also includes these types of augmentations for completeness and utility.
+Descriptions of all \emph{Augraphy} augmentations are available online, along with the motivation for their development and usage examples. \footnote{\url{https://augraphy.readthedocs.io/en/latest/}}
+
+\subsection{The Library}
 \emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners, and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
@@
 \noindent\textbf{\texttt{AugmentationResult}.} ~After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
-These objects also record a full copy of the augmentation runtime data, as well as any metadata that might be relevant for debugging or other advanced use.
+These also record a full copy of the augmentation runtime data, as well as any metadata that might be relevant for debugging or other advanced use.
 
 \smallskip
-\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
+\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
 In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
@@
 \begin{quote}
-The initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
-Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts.
-Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository.
+  \begin{enumerate}
+  \item Ink is adhered to the paper material during the initial printing of a document.
+  \item The document is attached to a public bulletin board in a high-traffic area.
+  \item Over a period of several weeks, it is annotated, defaced, and eventually torn away from its securing staples, flying away in the wind.
+  \item Fifty years later, our protagonist page is discovered by cleaning staff, who turn it over to library archivists.
+  \item These conservationists use delicate tools to gently position and record an image of the document, storing this in a digital repository.
+  \end{enumerate}
 \end{quote}
@@
 
-Realistically reproducing effects in document images requires rethinking how those effects are produced in the real world.
+Realistically reproducing effects in document images requires careful attention to how those effects are produced in the real world.
 Many issues, like the various forms of misprint, only affect text and images on the page.
@@
 Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.
-Effectively capturing processes like these in reproducible augmentations means separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
-Producing realistically noisy document images can now be reduced to the definition and application of one or more Augraphy pipelines to some clean document images.
+Effectively capturing processes like these in reproducible augmentations means separating our model of a document pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
+Producing realistically noisy document images can now be reduced to the definition and application of one or more Augraphy pipelines to some clean, born-digital document images.
 
-The value added by the \texttt{AugraphyPipeline} class over a bare list of functions mapped over an image is principally in the collection of runtime metadata:
-the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
+The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
 This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure 1 \ref{fig:intro}.
@@
 \smallskip
-There are also two classes that provide additional functionality in order to round out the \emph{Augraphy} base library:
+There are also two classes that provide additional critical functionality in order to round out the \emph{Augraphy} base library:
 
@@
 This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image.
-The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database.
+The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database \cite{ref_NoisyOfficeDatabase}.
 Taken together, \texttt{PaperFactory} makes it trivial to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.
@@
 %\smallskip
-\noindent\textbf{\texttt{ComposePipelines}.} ~This class provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.
+\noindent\textbf{\texttt{ComposePipelines}.} ~This class provides a means of composing two pipelines into one, allowing for the construction of complex multi-pipeline operations.
 
@@
 \smallskip
-\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for simulating ``printing".
+\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for ``printing" or applying other artifacts like staples or stamps.
 
@@
 
-\emph{Augraphy} pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
-
-After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
-Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
-
 \section{Deep Learning with Augraphy}
 Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
-This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data.
-We perform the same experiment twice, with different model designs.
-We continue to return to the NoisyOffice database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for analyzing Augraphy.
+This section describes a brief experiment in which Augraphy was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets.
+This corpus is used to train two denoising convolutional neural networks with different model designs, each of which makes high-accuracy predictions, demonstrating Augraphy's utility for robust data augmentation.
+
+All code used in these experiments is available in the Augraphy-Paper GitHub repository \footnote{\url{https://github.com/sparkfish/augraphy-paper}}.
 
@@
 We selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
-The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.
+The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, changing the batch size and learning epoch count to fit our training data.
 
 \subsection{Data Generation}
-Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.
+Despite recent techniques (\cite{ref_tvt2040}, \cite{ref_vtssds}) for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its capacity for generalization to new data.
 
-The NoisyOffice data provided by Kaggle contains 144 ground truth images, 144 training images, and 72 validation images.
-For the Augraphy model, we produced a dataset 10x larger, by duplicating each of the ground truth images, then running 10 Augraphy pipelines against each copy.
-Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.
+To train our model, we developed the ShabbyPages dataset \cite{ref_ShabbyPages}, a real-world document image corpus with Augraphy-generated synthetic noise.
+Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several workers across multiple days.
+Adding the noise to these images was trivial however; Augraphy makes it easy to produce large training sets.
+For additional realistic variation, we also gathered 300 paper textures and used the PaperFactory augmentation to ``print'' our source documents onto these.
 
-The NoisyOffice dataset contains folded sheets, wrinkled sheets, coffee stains, and footprint noise.
-The features given by the wrinkle and fold distortions can be mimicked by overlaying the foreground text on wrinkled and folded paper textures, as the NoisyOffice team did, and the features created by the stains and footprints can be mimicked by introducing dark regions and thin lines.
-With Augraphy, we expected that we could use the BadPhotoCopy augmentation to produce the dark regions and a combination of the strikethrough behavior from the Markup augmentation and the smooth curve shading behavior of the PencilScribbles augmentation to add the last feature to the ground-truth data.
-The PaperFactory augmentation makes the paper texture overlay trivial and repeatable. In the end, we executed the following pipeline:
+The initial 600 PDF documents were split into their component pages, totaling 6202 clean document images exported at 150 pixels per inch.
+We iteratively developed an Augraphy pipeline which produced satisfactory output with few overly-noised images, then ran each of the clean images through this to produce the base training set.
+Patches were taken from each of these images and used for the final training collection.
 
-\begin{lstlisting}[language=Python, label={lst:test-pipeline}, caption={Pipeline used for test data generation.}]
-ink_phase = []
-paper_phase = [PaperFactory(p=0.5)]
-post_phase = [
-  BadPhotoCopy(p=0.5),
-  PencilScribbles(p=0.5),
-  Markup(markup_color=(0,0,0), p=0.5)
-]
-AugraphyPipeline(ink_phase, paper_phase, post_phase)
-\end{lstlisting}
-
-In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.
-
-The PaperFactory augmentation reads and randomly crops image textures from a local directory; to this we added two \footnote{\url{https://p2.piqsels.com/preview/642/889/110/paper-crease-creased-texture.jpg}}, \footnote{\url{https://blog.miklavcic.si/wp-content/uploads/2011/11/white_paper_1.png}} public domain images of wrinkled paper found with Bing.
+Another new dataset --- Real ShabbyPages --- was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
+Real ShabbyPages is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating Augraphy's effect.
 
 \subsection{Training Regime}
-We fit the models described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.
+Training of the UNet model proceeded for 600 epochs, learning features from 1050 patches of 500x500 pixels.
 
-Training of the UNets proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs.
-The NoisyOffice model finished training after \numNoisyOfficeUNetEpochs epochs, while the Augraphy model trained for the full 600 epochs.
+The NAFNet was given a much larger sample to learn from: 10 square patches 400 pixels to a side were used to train this instance, across just 16 epochs.
 
@@
 
-The NAFNet instances trained for 100 epochs, using the default settings provided from the GitHub version.
-All code used in these experiments is available in the Augraphy-Paper GitHub \footnote{\url{https://github.com/sparkfish/augraphy-paper}}.
-
 \subsection{Results}
 Sample predictions from each model on the validation task are presented in Table 1.
-A new dataset, ShabbyPagesReal, was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
-ShabbyPagesReal is fully out-of-distribution for the models in our experiments, and has a much higher degree of diversity than the NoisyOffice set, providing good conditions for evaluating Augraphy's effect.
-As expected, the NoisyOffice models perform admirably, fitting extremely well to the low-diversity data of the NoisyOffice set, but they do struggle to fully remove the coffee stain feature, leaving some residue.
-The SSIM score indicates that the Augraphy models generalize much better, though they do overcompensate for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.
-
-%[TODO: is this true?] The Augraphy models clearly outperform the NoisyOffice models at stain removal, but do not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features.
+The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.
 
@@
 \includegraphics[width=\textwidth]{figures/sidebyside.png}
-\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
+\caption{Validation images (left), with the images predicted by the ShabbyPages_NAFNet (center) and ShabbyPages_NAFNet_large (right) models.}
 \end{figure} %[TODO: can we show this a better way?]
@@
 
-Over the last 5 epochs of training, the performance of the models on average loss, average mean-average-error (MAE), average validation loss, and average validation MAE were recorded.
-The models predicted cleaned versions of the validation images (Figure 4), which were then compared to the groundtruth versions according to each metric.
-The average over all such results obtained during validation was taken.
-These metrics are displayed in Table 1.
-
 \begin{table}
 \centering
-\caption{Model training statistics and performance on NoisyOffice validation task}\label{tab1}
+\caption{Model training statistics and performance on Real ShabbyPages validation task}\label{tab1}
 \begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
@@
 \hline
-NoisyOffice\_UNet & 63.09 & 0.87 & 0.19\\
 Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
-NoisyOffice\_NAFNet & & &
 Augraphy\_NAFNet & & &
+Augraphy\_NAFNet_large & & &
 \hline
@@
 
-The Augraphy model outperforms the PSNR score of the NoisyOffice model on the validation task by half a percent, and has a lower mean average error both in test and validation during training, but underperforms by 0.8\% on structural similarity and 2.5\% on RMSE in validation, with a higher average test and validation loss.
-These numbers are consistent with the visual prediction results displayed in Figure 1: the Augraphy model predicts fewer pixels in the text (RMSE lower by 2.5\%), but removes more noise and with a higher degree of fidelity than the NoisyOffice model (PSNR higher by 0.2576466946).
-The training metrics collected indicate that the Augraphy model has lower variance so is more precise than the NoisyOffice model, but exhibits higher loss and thus less accuracy in its predictions.
-
+[TODO: add numbers and interpretation]
 \section{Robustness Testing}
@@
 
-We use the widely-used open-source Tesseract 2 engine and first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known.
+We first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known.
 We then used Tesseract to generate OCR predictions on these noise-free documents, as a baseline for comparison.
@@
 
-We also described the process for creating new document image datasets that contain synthetic real-world noise using Augraphy, then compared results obtained by training a convolutional U-Net and a NAFNet on these datasets.
+We described the process for using Augraphy to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional U-Net and two NAFNet instances on this corpus.
 
-Future work on the Augraphy library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on more common hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions and responding to community-initiated feature requests.
+Finally, we examined Augraphy's efficacy in generating confounding data for testing the robustness of document vision models.
+
+Future work on the Augraphy library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on commodity hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions, and responding to community-initiated feature requests.
 

### 2023-02-10 paper.tex

@@
 
+\subsection{Face Detection Robustness Testing}
+In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
+Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
+In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
+Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
+
+\begin{wraptable}{r}{5cm}
+    \centering
+    \caption{Face detection performance.}
+    \begin{tabular}{lr}
+    \toprule
+        \textbf{Model} & \textbf{Accuracy} \\
+        \midrule
+        Azure & 57.1\%\\
+        Google & 60.1\%  \\
+        Amazon & 49.1\% \\
+        UltraFace & 4.5\%\\
+        \bottomrule
+    \end{tabular}
+    \label{tab:face-detection-results}
+\end{wraptable}
+
+We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}.
+Then, we use \emph{Augraphy} to generate 10 altered versions of each image and manually remove any augmented image where the face(s) is not reasonably visible.
+We then test four face detection models on the noisy and noise-free images.
+These models are: proprietary face detection models from Google,\footnote{\url{https://cloud.google.com/vision/docs/detecting-faces}} Amazon,\footnote{\url{https://aws.amazon.com/rekognition/}} and Microsoft\footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services/face}}, and lastly the freely-available UltraFace\footnote{\url{https://github.com/onnx/models/tree/main/vision/body_analysis/ultraface}} model.
+%We then test Microsoft Azure's face detection model on the noise-free and noisy images.
+
+Table~\ref{tab:face-detection-results} shows face detection accuracy of both models on the noisy test set, and example images where no faces were detected by the Microsoft model are shown in Figure \ref{fig:face-detection-mistakes}.
+We see that all four models struggle on the \emph{Augraphy}-augmented data, with the proprietary models seeing detection performances drop to between roughly 50-60\%, and UltraFace detecting only 4.5\% of faces that it found in the noise-free data.
+
+\begin{figure}
+    \centering\scalebox{0.47}{
+    \includegraphics{figures/azure_1x3_face_errors.pdf}}
+    \caption{Example augmented images that yielded false-positive predictions with the Azure face detector.}
+    \label{fig:face-detection-mistakes}
+\end{figure}
+
 %% [TODO: render this]

### 2023-02-10 paper.tex
bugfix wrapfig and complete table
Minor formatting adjustments

@@
 \usepackage{tabularx}
+\usepackage{sectsty}
+\usepackage{wrapfig}
 \AtBeginEnvironment{quote}{\par\singlespacing\small}
@@
                 \includegraphics{figures/archetype-memo.pdf}}}      \\
-        (a) & (b) & (c) \\
+        %(a) & (b) & (c) \\
     \end{tabularx}
@@
 \emph{Augraphy} has been used in several research efforts: Larson et al.
-(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document deniosing GAN; and Kim et al.
+(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al.
 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
@@
     \midrule
-        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
+        \emph{Augmentor} \cite{augmentor} & 27 & \xmark & \cmark  & \cmark & MIT \\
         \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
         \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
-        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
+        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & \cmark & \cmark & MIT \\
         \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
@@
 \section{Document Distortion, Theory \& Technique}
-Many approaches exist for adding features to an image, and many types of feature can be generated.
-The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\
+Many approaches exist for adding features to an image, and many types of features can be generated.
+The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.
 
@@
 The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations.
-Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\
+Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.
 
 Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
-Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.\\
+Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.
 
@@
 \item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
-\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
+\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation.
+DocCreator's 3D mesh support here is excellent and has inspired Augraphy to add similar functionality in its roadmap.
+In the meantime, Augraphy currently offers support for paper folds.
 \end{enumerate}
-
-Augraphy already has a story for the first three, with the fourth in planning.
 
@@
 The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
-This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure 1 \ref{fig:intro}.
+ This pipeline metadata allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.
 
-\smallskip
+\sectionfont{\keepall}
 There are also two classes that provide additional critical functionality in order to round out the \emph{Augraphy} base library:
@@
 
-\smallskip
+\sectionfont{\normalfont}
 \noindent\textbf{\texttt{PaperFactory}.} ~We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.

### 2023-02-10 paper.tex
Updated styling of Augraphy references; added ShabbyPages citation

@@
 \begin{abstract}
-This paper introduces Augraphy, a Python library for constructing data augmentation pipelines which produce distortions commonly seen in real-world document image datasets.
-Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
-This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and also for generating challenging test data to evaluate model robustness on document image modeling tasks.
+This paper introduces \emph{Augraphy}, a Python library for constructing data augmentation pipelines which produce distortions commonly seen in real-world document image datasets.
+\emph{Augraphy} stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
+This paper discusses the \emph{Augraphy} tool, and shows how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document denoising, and also for generating challenging test data to evaluate model robustness on document image modeling tasks.
 
@@
     \begin{tabularx}{\linewidth}{*{3}{>{\centering\arraybackslash}X}}
-        Noisy Original & Clean Reproduction & Augraphy Reproduction \\
+        Noisy Original & Clean Reproduction & \emph{Augraphy} Reproduction \\
         \multicolumn{3}{c}{
@@
     \caption{Comparison of various image-based data augmentation libraries.
-Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities.
-Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
+Number of augmentations is a rough count, and many augmentations in other tools are what \emph{Augraphy} calls Utilities.
+Further, many single augmentations in \emph{Augraphy} --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
     \resizebox{0.9\textwidth}{!}{
@@
 
-Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
+\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
 Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.
@@
 \item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation.
-DocCreator's 3D mesh support here is excellent and has inspired Augraphy to add similar functionality in its roadmap.
-In the meantime, Augraphy currently offers support for paper folds.
+DocCreator's 3D mesh support here is excellent and has inspired \emph{Augraphy} to add similar functionality in its roadmap.
+In the meantime, \emph{Augraphy} currently offers support for paper folds.
 \end{enumerate}
@@
 \includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background}
+\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
 \label{fig:pipeline}
@@
 
-Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations, listed in Table~\ref{tab:augmentations}.
+\emph{Augraphy} provides \numAugraphyAugmentations ~out-of-the-box augmentations, listed in Table~\ref{tab:augmentations}.
 As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
@@
 Effectively capturing processes like these in reproducible augmentations means separating our model of a document pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
-Producing realistically noisy document images can now be reduced to the definition and application of one or more Augraphy pipelines to some clean, born-digital document images.
+Producing realistically noisy document images can now be reduced to the definition and application of one or more \emph{Augraphy} pipelines to some clean, born-digital document images.
 
@@
 \includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
-\caption{Examples of some Augraphy augmentations.} \label{fig2}
+\caption{Examples of some \emph{Augraphy} augmentations.} \label{fig2}
 \end{figure}
 
-\section{Deep Learning with Augraphy}
-Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
-This section describes a brief experiment in which Augraphy was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets.
-This corpus is used to train two denoising convolutional neural networks with different model designs, each of which makes high-accuracy predictions, demonstrating Augraphy's utility for robust data augmentation.
+\section{Deep Learning with \emph{Augraphy}}
+\emph{Augraphy} aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
+This section describes a brief experiment in which \emph{Augraphy} was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets.
+This corpus is used to train two denoising convolutional neural networks with different model designs, each of which makes high-accuracy predictions, demonstrating \emph{Augraphy}'s utility for robust data augmentation.
 
-All code used in these experiments is available in the Augraphy-Paper GitHub repository \footnote{\url{https://github.com/sparkfish/augraphy-paper}}.
+All code used in these experiments is available in the \texttt{augraphy-paper} GitHub repository \footnote{\url{https://github.com/sparkfish/augraphy-paper}}.
 
 \subsection{Model Architecture}
-To evaluate Augraphy, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}.
+To evaluate \emph{Augraphy}, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}.
 We selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
@@
 
-To train our model, we developed the ShabbyPages dataset \cite{ref_ShabbyPages}, a real-world document image corpus with Augraphy-generated synthetic noise.
+To train our model, we developed the ShabbyPages dataset \cite{ref_ShabbyPages}, a real-world document image corpus with \emph{Augraphy}-generated synthetic noise.
 Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several workers across multiple days.
-Adding the noise to these images was trivial however; Augraphy makes it easy to produce large training sets.
+Adding the noise to these images was trivial however; \emph{Augraphy} makes it easy to produce large training sets.
 For additional realistic variation, we also gathered 300 paper textures and used the PaperFactory augmentation to ``print'' our source documents onto these.
@@
 The initial 600 PDF documents were split into their component pages, totaling 6202 clean document images exported at 150 pixels per inch.
-We iteratively developed an Augraphy pipeline which produced satisfactory output with few overly-noised images, then ran each of the clean images through this to produce the base training set.
+We iteratively developed an \emph{Augraphy} pipeline which produced satisfactory output with few overly-noised images, then ran each of the clean images through this to produce the base training set.
 Patches were taken from each of these images and used for the final training collection.
 
-Another new dataset --- Real ShabbyPages --- was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
-Real ShabbyPages is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating Augraphy's effect.
+Another new dataset --- ShabbyReal --- was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
+ShabbyReal is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
 
@@
 \centering
-\caption{Model training statistics and performance on Real ShabbyPages validation task}\label{tab1}
+\caption{Model training statistics and performance on ShabbyReal validation task}\label{tab1}
 \begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
@@
 \section{Robustness Testing}
-We use Augraphy to add noise to an image of text with known groundtruth.
-The Tesseract \cite{ref_tesseract} pre-trained OCR model's performance on the clean image is compared to the OCR result on the Augraphy-noised image, then to the true groundtruth string, using the Levenshtein distance.
-These measures are averaged over 1000 trials, with different Augraphy effects, to give some indication of Augraphy's effect on producing human-readable document images for challenging OCR tasks.
+We use \emph{Augraphy} to add noise to an image of text with known groundtruth.
+The Tesseract \cite{ref_tesseract} pre-trained OCR model's performance on the clean image is compared to the OCR result on the \emph{Augraphy}-noised image, then to the true groundtruth string, using the Levenshtein distance.
+These measures are averaged over 1000 trials, with different \emph{Augraphy} effects, to give some indication of \emph{Augraphy}'s effect on producing human-readable document images for challenging OCR tasks.
 
@@
 We considered these OCR predictions as the ground-truth labels for each document.
-Next, we generated noisy versions of the 15 documents by running them through an Augraphy pipeline, and again used Tesseract to generate OCR predictions on these noisy documents.
+Next, we generated noisy versions of the 15 documents by running them through an \emph{Augraphy} pipeline, and again used Tesseract to generate OCR predictions on these noisy documents.
 We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%.
-This example use-case demonstrates the effectiveness of using Augraphy to create challenging test data for evaluating OCR systems.
+This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data for evaluating OCR systems.
 
@@
 %% \includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
-%% \caption{Groundtruth image (left), sample of Augraphy output (right).} \label{fig5}
+%% \caption{Groundtruth image (left), sample of \emph{Augraphy} output (right).} \label{fig5}
 %% \end{figure}
@@
 %%     \toprule
-%%     \textbf{Groundtruth String} & \textbf{OCR output on clean image \\ distance to true string} & \textbf{Average OCR output on Augraphy-noised images \\ distance to true string} \\
+%%     \textbf{Groundtruth String} & \textbf{OCR output on clean image \\ distance to true string} & \textbf{Average OCR output on \emph{Augraphy}-noised images \\ distance to true string} \\
 %%     \midrule
@@
 
-%% In Table 3 \ref{tab:levenshtein}, it can be seen that Augraphy introduces features which confound the Tesseract pre-trained OCR model.
+%% In Table 3 \ref{tab:levenshtein}, it can be seen that \emph{Augraphy} introduces features which confound the Tesseract pre-trained OCR model.
 
 \section{Conclusion and Future Work}
-We presented Augraphy, a framework for generating realistic synthetically-augmented datasets of document images.
+We presented \emph{Augraphy}, a framework for generating realistic synthetically-augmented datasets of document images.
 Other available image augmentation tools were examined and found to lack features needed for our purposes, motivating the creation of this library specifically targeting the types of alterations and degradations seen in document images.
 
-We described the process for using Augraphy to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional U-Net and two NAFNet instances on this corpus.
+We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional U-Net and two NAFNet instances on this corpus.
 
-Finally, we examined Augraphy's efficacy in generating confounding data for testing the robustness of document vision models.
+Finally, we examined \emph{Augraphy}'s efficacy in generating confounding data for testing the robustness of document vision models.
 
-Future work on the Augraphy library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on commodity hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions, and responding to community-initiated feature requests.
+Future work on the \emph{Augraphy} library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on commodity hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions, and responding to community-initiated feature requests.
 
-Augraphy is licensed under the MIT open source license, and readers are invited to share feedback and participate in its development on GitHub.
+\emph{Augraphy} is licensed under the MIT open source license, and readers are invited to share feedback and participate in its development on GitHub.
 

### 2023-02-10 paper.tex
Added styling to Shabby references throughout

@@
 
-To train our model, we developed the ShabbyPages dataset \cite{ref_ShabbyPages}, a real-world document image corpus with \emph{Augraphy}-generated synthetic noise.
-Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several workers across multiple days.
+To train our model, we developed the \emph{ShabbyPages} dataset \cite{ref_ShabbyPages}, a real-world document image corpus with \emph{Augraphy}-generated synthetic noise.
+Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several crowdworkers across multiple days.
 Adding the noise to these images was trivial however; \emph{Augraphy} makes it easy to produce large training sets.
@@
 
-Another new dataset --- ShabbyReal --- was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
-ShabbyReal is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
+Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
+\emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
 
@@
 \centering
-\caption{Model training statistics and performance on ShabbyReal validation task}\label{tab1}
+\caption{Model training statistics and performance on \emph{ShabbyReal} validation task}\label{tab1}
 \begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
@@
 We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%.
-This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data for evaluating OCR systems.
+This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data that remains human readable suitable for evaluating OCR systems.
 

### 2023-02-11 paper.tex
cleanup whitespace
update table template for shabbyreal denoising metrics
Update paper.tex
- Remove ImageOverlay since we are not using that.
- Added NoiseGenerator.

@@
 \smallskip
-\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for ``printing" or applying other artifacts like staples or stamps.
+\noindent\textbf{\texttt{OverlayBuilder}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for ``printing" or applying other artifacts like staples or stamps.
+
+\smallskip
+\noindent\textbf{\texttt{NoiseGenerator}.} ~This class uses make blobs algorithm to generate mask of noises in different shape and location.
 
@@
 \centering
-\caption{Model training statistics and performance on \emph{ShabbyReal} validation task}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
+\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
+\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
 \hline
-Metric & PSNR & SSIM & RMSE\\
+Metric & Score \\
 \hline
-Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
-Augraphy\_NAFNet & & &
-Augraphy\_NAFNet_large & & &
+SSIM & \\
+PSNR & \\
+RMSE & \\
 \hline

### 2023-02-11 paper.tex
update OCR section with image, better intro

--- 2023-02-10 paper.tex
@@
 \newcommand{\numNoisyOfficeUNetEpochs}{\emph{426}}
-\newcommand{\ocrCleanLevenshteinDistance}{\emph{TODO}}
-\newcommand{\ocrAugraphyAverageLevenshteinDistance}{\emph{TODO}}
 
@@
 \section{Robustness Testing}
-We use \emph{Augraphy} to add noise to an image of text with known groundtruth.
-The Tesseract \cite{ref_tesseract} pre-trained OCR model's performance on the clean image is compared to the OCR result on the \emph{Augraphy}-noised image, then to the true groundtruth string, using the Levenshtein distance.
-These measures are averaged over 1000 trials, with different \emph{Augraphy} effects, to give some indication of \emph{Augraphy}'s effect on producing human-readable document images for challenging OCR tasks.
+In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.
 
+One of \emph{Augraphy}'s \emph{raisons d'être} is denoising identity documents like driver's licenses, passports, and immigration forms; images of these documents are often generated in high-traffic environments like emergency rooms or border checkpoints, where the image capture hardware is frequently dirty or malfunctioning, producing noisy outputs.
+Accurately capturing information is extremely important in these settings for human health and security, necessitating robust denoising and object detection models.
+
+We first use \emph{Augraphy} to add noise to an image of text with known groundtruth.
+The Tesseract \cite{ref_tesseract} pre-trained OCR model's performance on the clean image is compared to the OCR result on the \emph{Augraphy}-noised image using the Levenshtein distance.
+
+Then, we add \emph{Augraphy}-generated noise to document images which contain pictures of people, and perform face-detection on the output, comparing the detection accuracy to that of the clean images.
+
+\subsection{Character Recognition}
 We first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known.
@@
 This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data that remains human readable suitable for evaluating OCR systems.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth, frame]{figures/ocr_figure.png}
+\caption{Sample \emph{ShabbyReal} clean/noisy image pair, and the OCR output for each. The computed Levenshtein distance between the OCR result strings is 203.}
+\label{fig:ocr_output}
+\end{figure}
 
@@
 
-%% [TODO: render this]
-%% \begin{figure}
-%% \includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
-%% \caption{Groundtruth image (left), sample of \emph{Augraphy} output (right).} \label{fig5}
-%% \end{figure}
-
-%% [TODO: get results]
-%% \begin{table}[]
-%%     \centering
-%%     \caption{Measuring \emph{Augraphy}'s effect on OCR model performance.}
-%%     \scalebox{0.81}{
-%%     \begin{tabular}{lll}
-%%     \toprule
-%%     \textbf{Groundtruth String} & \textbf{OCR output on clean image \\ distance to true string} & \textbf{Average OCR output on \emph{Augraphy}-noised images \\ distance to true string} \\
-%%     \midrule
-%%     "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum." & \ocrCleanLevenshteinDistance & \ocrAugraphyAverageLevenshteinDistance
-%%     \bottomrule
-%%     \end{tabular}}
-%%     \label{tab:levenshtein}
-%% \end{table}
-
-%% In Table 3 \ref{tab:levenshtein}, it can be seen that \emph{Augraphy} introduces features which confound the Tesseract pre-trained OCR model.
-
 \section{Conclusion and Future Work}

### 2023-02-11 paper.tex
have paper title match easychair title

@@
 
-\title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
+\title{Augraphy: A Data Augmentation Library for Document Images}
 %\author{Alexander Groleau\inst{1,2} \and
@@
 
-    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP.
-We re-created a clean version of (a) in (b).
-We then create a noisy version of (b) by applying several augmentations to it to produce (c).}
+    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP.
+We re-created a clean reproduction and then created a noisy version by applying several \emph{Augraphy} augmentations.}
 
@@
 
-A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
-These are cut to size and stacked, then bound in reams and sent out for sale and use.
-This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream.
-At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink.
-Any of these processes may alter the local texture or global topology of the sheet.
-The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations.
-Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.
-
-\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.
-Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.
+\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle at seen in the real world.
+Such real-world conditions and  features have direct implementations either within the library or on the development roadmap.
 
@@
 \begin{enumerate}
-\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
+\item Text can be generated independently of the paper texture, and can be overlaid onto the ``paper'' by a number of blending functions, allowing a variety of paper textures to be used.
 \item Similarly, any markup features may be generated and overlaid by the same methods.
@@
 
-There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.
-
-We now discuss each of these:
+There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality:
 
@@
 This section describes a brief experiment in which \emph{Augraphy} was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets.
-This corpus is used to train two denoising convolutional neural networks with different model designs, each of which makes high-accuracy predictions, demonstrating \emph{Augraphy}'s utility for robust data augmentation.
+This collection was used to train a denoising convolutional neural network capable of high-accuracy predictions, demonstrating \emph{Augraphy}'s utility for robust data augmentation.
 
@@
 \subsection{Model Architecture}
-To evaluate \emph{Augraphy}, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}.
-We selected this one for its simplicity and the clarity of its exposition, and use it with few changes.
-The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, changing the batch size and learning epoch count to fit our training data.
+To evaluate \emph{Augraphy}, we used an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}, making only minor alterations to the model's training hyperparameters, changing the batch size and learning epoch count to fit our training data.
 
 \subsection{Data Generation}
-Despite recent techniques (\cite{ref_tvt2040}, \cite{ref_vtssds}) for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its capacity for generalization to new data.
+Despite recent techniques (\cite{ref_tvt2040}, \cite{ref_vtssds}) for reducing the volume of input data required to train models, large datasets remain king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model to noise and increasing its capacity for generalization to new data.
 
@@
 Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
-\emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
+\emph{ShabbyReal} is fully out-of-distribution for this experiment, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
 
 \subsection{Training Regime}
-Training of the UNet model proceeded for 600 epochs, learning features from 1050 patches of 500x500 pixels.
+The NAFNet was given a large sample to learn from: for each image in the ShabbyPages set, we sampled ten patches of 400x400 pixels, using these to train the instance across just 16 epochs.
 
-The NAFNet was given a much larger sample to learn from: 10 square patches 400 pixels to a side were used to train this instance, across just 16 epochs.
-
-Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.
+The model was trained with mean squared error as the loss function, using the Adam optimizer and cosine annealing learning rate scheduler, then evaluated with the mean average error metric.
 
 \subsection{Results}
-Sample predictions from each model on the validation task are presented in Table 1.
+Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}.
 The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.
 
-\begin{figure}\label{fig4}
-\includegraphics[width=\textwidth]{figures/sidebyside.png}
-\caption{Validation images (left), with the images predicted by the ShabbyPages_NAFNet (center) and ShabbyPages_NAFNet_large (right) models.}
-\end{figure} %[TODO: can we show this a better way?]
-
-To compare the models' performance on the validation task, we considered the following metrics:
-\begin{enumerate}
-\item Root mean square error (RMSE)
-\item Structural similarity index (SSIM)
-\item Peak signal-to-noise ratio (PSNR)
-\end{enumerate}
+To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.
 
@@
 \caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
-\hline
-Metric & Score \\
-\hline
-SSIM & \\
-PSNR & \\
-RMSE & \\
+\begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
+\toprule
+\textbf{Metric} & \textbf{Score} \\
+\midrule
+SSIM & 0.71\\
+PSNR & 32.52\\
+RMSE & 6.52\\
 \hline
@@
 
-[TODO: add numbers and interpretation]
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
+\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
+\label{fig:shabbyreal_denoised}
+\end{figure}
+
+As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
+\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
+\label{fig:shabbypages_denoising}
+\end{figure}
+
 \section{Robustness Testing}
 In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.
-
-One of \emph{Augraphy}'s \emph{raisons d'être} is denoising identity documents like driver's licenses, passports, and immigration forms; images of these documents are often generated in high-traffic environments like emergency rooms or border checkpoints, where the image capture hardware is frequently dirty or malfunctioning, producing noisy outputs.
-Accurately capturing information is extremely important in these settings for human health and security, necessitating robust denoising and object detection models.
 
@@
 \subsection{Face Detection Robustness Testing}
-In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
-Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
-In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
-Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
-
-\begin{wraptable}{r}{5cm}
+\begin{wraptable}{r}{6cm}
     \centering
@@
 \end{wraptable}
+In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
+Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
+In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
+Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
 
@@
 
-We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional U-Net and two NAFNet instances on this corpus.
+We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.
 

### 2023-02-11 paper.tex
remove unet, fix training regime, add shabbyreal experiment data

--- 2023-02-11 paper.tex
@@
 Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.
-\emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
+\emph{ShabbyReal} is fully out-of-distribution for this experiment, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.
 
 \subsection{Training Regime}
-Training of the UNet model proceeded for 600 epochs, learning features from 1050 patches of 500x500 pixels.
+The NAFNet was given a large sample to learn from: for each image in the ShabbyPages set, we sampled ten patches of 400x400 pixels, using these to train the instance across just 16 epochs.
 
-The NAFNet was given a much larger sample to learn from: 10 square patches 400 pixels to a side were used to train this instance, across just 16 epochs.
-
-Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.
+The model was trained with mean squared error as the loss function, using the Adam optimizer and cosine annealing learning rate scheduler, then evaluated with the mean average error metric.
 
 \subsection{Results}
-Sample predictions from each model on the validation task are presented in Table 1.
+Sample predictions from the model on the validation task are presented in Figure \cite{fig:shabbyreal_denoising}.
 The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.
 
-\begin{figure}\label{fig4}
-\includegraphics[width=\textwidth]{figures/sidebyside.png}
-\caption{Validation images (left), with the images predicted by the ShabbyPages_NAFNet (center) and ShabbyPages_NAFNet_large (right) models.}
-\end{figure} %[TODO: can we show this a better way?]
-
-To compare the models' performance on the validation task, we considered the following metrics:
-\begin{enumerate}
-\item Root mean square error (RMSE)
-\item Structural similarity index (SSIM)
-\item Peak signal-to-noise ratio (PSNR)
-\end{enumerate}
+To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.
 
@@
 \hline
-SSIM & \\
-PSNR & \\
-RMSE & \\
+SSIM & 0.71\\
+PSNR & 32.52\\
+RMSE & 6.52\\
 \hline
@@
 
-[TODO: add numbers and interpretation]
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
+\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
+\label{fig:shabbyreal_denoised}
+\end{figure}
+
+As can be seen in  Figure \cite{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
+
 \section{Robustness Testing}

### 2023-02-11 paper.tex
change figure links to refs

@@
 \subsection{Results}
-Sample predictions from the model on the validation task are presented in Figure \cite{fig:shabbyreal_denoising}.
+Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoising}.
 The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.
@@
 
-As can be seen in  Figure \cite{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
+As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
 

### 2023-02-11 paper.tex
Chopping some un-needed text to allow space for more images

@@
 
-One of \emph{Augraphy}'s \emph{raisons d'être} is denoising identity documents like driver's licenses, passports, and immigration forms; images of these documents are often generated in high-traffic environments like emergency rooms or border checkpoints, where the image capture hardware is frequently dirty or malfunctioning, producing noisy outputs.
-Accurately capturing information is extremely important in these settings for human health and security, necessitating robust denoising and object detection models.
-
 We first use \emph{Augraphy} to add noise to an image of text with known groundtruth.

### 2023-02-11 paper.tex
add shabbypages denoised image
fix shabbyreal_denoised ref

@@
 \subsection{Results}
-Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoising}.
+Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}.
 The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.
@@
 As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
+\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
+\label{fig:shabbypages_denoising}
+\end{figure}
 

### 2023-02-11 paper.tex
table fixes

--- 2023-02-11 paper.tex
@@
 \caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
-\hline
-Metric & Score \\
-\hline
+\begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
+\toprule
+\textbf{Metric} & \textbf{Score} \\
+\midrule
 SSIM & 0.71\\

### 2023-02-11 paper.tex
space
Updates from Overleaf
Spelling correction

@@
 
-\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle at seen in the real world.
+\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle as seen in the real world.
 Such real-world conditions and  features have direct implementations either within the library or on the development roadmap.
@@
 \centering
-\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
+\includegraphics[width=0.9\columnwidth]{figures/shabbyreal_denoised.png}
 \caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
@@
 \centering
-\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
+\includegraphics[width=0.95\columnwidth]{figures/shabbypages_denoising.png}
 \caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
@@
 \centering
-\includegraphics[width=0.98\columnwidth, frame]{figures/ocr_figure.png}
+\includegraphics[width=0.9\columnwidth, frame]{figures/ocr_figure.png}
 \caption{Sample \emph{ShabbyReal} clean/noisy image pair, and the OCR output for each. The computed Levenshtein distance between the OCR result strings is 203.}

### 2023-02-11 paper.tex
Minor updates

@@
 \emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
-Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
+Users of the library can define directed acyclic graphs of images and their transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
 

### 2023-04-22 paper.tex
Remove anonymous header
Updated intro and motivation

@@
 \title{Augraphy: A Data Augmentation Library for Document Images}
-%\author{Alexander Groleau\inst{1,2} \and
-%Kok Wei Chee\inst{1} \and
-%Samay Maini\inst{1} \and
-%Jonathan Boarman\inst{1}}
-%
-%\authorrunning{A. Groleau et al.}
-%
-%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
-%\and
-%Left Associates LLC (\email{research@left.associates})}
+\author{Alexander Groleau\inst{1} \and
+Kok Wei Chee\inst{1} \and
+Stefan Larson\inst{2} \and
+Samay Maini\inst{1} \and
+Jonathan Boarman\inst{1}}
 
-\author{Anonymous ICDAR 2023 submission}
+\authorrunning{A. Groleau et al.}
+
+\institute{Sparkfish LLC (\email{augraphy@sparkfish.com}) \and
+Vanderbilt University}
 
@@
 \section{Introduction and Motivation}
-Daily life in the modern world is increasingly data-driven, involving myriad tasks which require the generation and handling of unstructured data.
-Increasingly, this data occurs in the form of messages or images, often with complex contents.
-In the office space, most data is created and stored document-form, easy to print and distribute.
-The lifetime of these documents typically includes physical alterations by printing, scanning, or photocopying operations, so real documents may appear visually very different from their original born-digital counterparts.
-Real-world processes can introduce many types of distortions: folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; human-made annotations like highlighting or pencil marks can add noise to the page.
 
-The outcomes of many machine learning operations involving documents are impacted by the presence of such noise; high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
-For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
-Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
-The lower-level task of document denoising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
-All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation, reducing the need for human toil.
+The \emph{Augraphy} library is designed to produce training datasets, pairing synthetic dirty documents with their clean ground truth document image sources.
+The need for such a data augmentation tool in document image analysis primarily results from the lack of ground truth images being available for most of the documents recorded within human history.
+Access to the knowledge stored in such document images is thwarted by artifacts, distortion and noise.
+As such, there is an ongoing need to improve available techniques to restore document images and thereby unlocking their contents for use in search or other document analysis tasks.
+
+An ongoing digital transformation has reduced everyday reliance on paper.
+However, major industries such as healthcare\cite{menachemi2011benefits}, insurance\cite{gatzert2016impact}, legal\cite{staudt2015access}, financial services\cite{chuen2017handbook}, government\cite{albano2018role}, and education\cite{alkhezzi2020factors} continue to produce physical documents that are later digitally archived.
+
+Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and daily life.
+Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, degraded text where low ink, annotations, highlighters or other markings add noise to the page that perturb semantic access by digital means.
 
@@
     \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP.
-We re-created a clean reproduction and then created a noisy version by applying several \emph{Augraphy} augmentations.}
+We demonstrate this by creating a noisy reproduction via \emph{Augraphy} augmentations against a clean reproduction.}
 
@@
 
+Document image analysis tasks are impacted by the presence of such noise; high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
+For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
+Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
+
+Attempts have been made to denoise document images in order to improve document tasks \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
+However, they have lacked the benefit of large datasets with ground truth images to train those denoisers.
+
+A tool such as \emph{Augraphy} that helps to produce copious amounts of training data with document noise artefacts is essential in this space to developing advanced document binarization and denoising processes.
+
 For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office procedures.
 \emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
+
 \emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
-The resulting images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
+The resulting images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
 
-\emph{Augraphy} has been used in several research efforts: Larson et al.
+Several research efforts have used \emph{Augraphy}: Larson et al.
 (2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al.
 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
-
-This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.
 

### 2023-04-29 paper.tex
Updated related work section

@@
 An ongoing digital transformation has reduced everyday reliance on paper.
-However, major industries such as healthcare\cite{menachemi2011benefits}, insurance\cite{gatzert2016impact}, legal\cite{staudt2015access}, financial services\cite{chuen2017handbook}, government\cite{albano2018role}, and education\cite{alkhezzi2020factors} continue to produce physical documents that are later digitally archived.
+However, major industries such as healthcare~\cite{menachemi2011benefits}, insurance~\cite{gatzert2016impact}, legal~\cite{staudt2015access}, financial services~\cite{chuen2017handbook}, government~\cite{albano2018role}, and education~\cite{alkhezzi2020factors} continue to produce physical documents that are later digitally archived.
 
@@
 
-This section discusses prior work related to data augmentation and robustness testing, especially as it relates to document understanding and processing tasks.
+This section reviews prior work on data augmentation and available tooling for robustness testing, particularly in the context of document understanding, processing, and analysis tasks.
+
+Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools.
+This analysis highlights that most existing data augmentation libraries do not specifically cater to the corruptions typically encountered in document image analysis datasets.
+In contrast, \emph{Augraphy} is designed to be easily integrated into machine learning pipelines alongside popular Python packages used in machine learning and document analysis.
+Our paper also utilizes robustness testing to demonstrate how \emph{Augraphy} can be used to evaluate a model's effectiveness in the face of challenging conditions.
+Instead of general image modifications, we focus on document-specific distortions and alterations that are better suited to challenge OCR models with document images that still retain sufficient quality to remain human-readable.
 
@@
 A wide variety of data augmentation tools and pipelines exist for machine learning tasks, including  natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
-In the latter realm, popular tools include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, and \emph{imgaug} \cite{ref_imgaug}.
-Augmentation strategies from these image-centric libraries are typically general-purpose, and include transformations like rotations, warps, and color modifications.
-Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools.
-As can be seen, these other data augmentation libraries do not specifically provide support for imitating the corruptions commonly seen in document analysis corpora.
 
-A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
-\emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
-The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate noise caused by office room procedures.
-\emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
-\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_pytorch}.
+As it pertains to computer vision, popular tools such as \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, and \emph{imgaug} \cite{ref_imgaug} provide image-centric augmentation strategies including general-purpose transformations like rotations, warps, masking, and color modifications.
+In contrast, as seen in Table~\ref{tab:augmentation-library-comparison}, only \emph{Augraphy} offers a data augmentation library that supports imitating the corruptions commonly seen in document analysis corpora and is also easily integrated in modern machine learning training processes which rely on Python, including use of specialized paper, ink and post-processing pipelines not seen elsewhere.
+In fact, we attempted to recreate the document in Figure~\ref{fig:intro} using \emph{Albumentations} in preparation for presenting such a comparison in this paper, but the results were so poor and unlike the target we aimed to reproduce that we felt our effort would not have been taken seriously.
+
+\emph{DocCreator}~\cite{ref_DocCreator} is the next best option, which provides an image-synthesizing tool for creating synthetic images that mimic common corruptions seen in document collections.
+However, \emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
+The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate a wider variety of both historical and modern scenarios.
+\emph{DocCreator} was also written in the C++ programming language as a monolithic \emph{what-you-see-is-what-you-get (WYSIWYG)} tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
+\emph{Augraphy}, on the other hand, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch~\cite{ref_pytorch}.
 

### 2023-04-29 paper.tex
Cuts and reorganization of text to get down to 15 pages

@@
 
-The introduction of noise-like corruptions and other modifications to image data can be used as a way of estimating and evaluating model robustness.
-Prior work in this space includes the use of image blurring, contrast and brightness changes, color alterations, partial occlusions, geometric transformations, pixel-level noise (e.g., salt-and-pepper noise, impulse noise, etc.), and compression artefacts (e.g., JPEG) to evaluate image classification and object detection models (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
+Testing a model's robustness with challenging datasets is a vital step to evaluate a model's resilience against real-world scenarios, helping developers identify and address weaknesses for enhanced effectiveness in document processing tasks.
+
+Prior work for evaluating image classification and object detection models includes image blur; contrast, brightness and color alterations; masking; geometric transforms; pixel-level noise; and JPEG compression artefacts (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
 More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
-Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications to produce human-readable distortions which challenge OCR models.
+Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, using specialized document-centric alterations to produce human-readable distortions which challenge OCR and face-detection models.
 
 \section{Document Distortion, Theory \& Technique}
-Many approaches exist for adding features to an image, and many types of features can be generated.
-The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.
-
-These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.
+As referenced in the \emph{Related Work} section of this paper, many general-purpose image distortion techniques exist for data augmentation and robustness testing.
+While these techniques are useful in general image analysis and understanding, they bear little resemblance to the features commonly found in real-world documents.
 
@@
 
+\begin{figure}
+\centering
+\scalebox{0.3}{
+\includegraphics[]{figures/pipeline.png}}
+\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
+\label{fig:pipeline}
+\end{figure}
+
+\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
+The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".
+
+The paper phase applies transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
+After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
+
+After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
+Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
+Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
+
 \section{Augraphy}
-This section dives into detail about the \emph{Augraphy} library.
-We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.
-
-\subsection{Overview}
 
@@
 
-Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
-
 \emph{Augraphy} is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
@@
 Users of the library can define directed acyclic graphs of images and their transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
-
-\begin{figure}
-\centering
-\scalebox{0.3}{
-\includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
-\label{fig:pipeline}
-\end{figure}
-
-\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
-The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".
-
-The paper phase applies transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
-After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-
-After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
-Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
 
@@
 \subsection{The Library}
-\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners, and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
-When composed, augmentations from the library interact to produce complex document image transformations, generating realistic new synthetically-augmented document images.
-
-There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality:
+There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality that when composed generate realistic synthetically-augmented document images:
 
@@
 Producing realistically noisy document images can now be reduced to the definition and application of one or more \emph{Augraphy} pipelines to some clean, born-digital document images.
-
-The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
- This pipeline metadata allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.
 

### 2023-04-29 paper.tex
unburied ledes, reworded/arranged sections, shortened, reformatted

@@
 
-\newcommand{\numAugraphyAugmentations}{\emph{26}}
+\newcommand{\numAugraphyAugmentations}{\emph{30}}
 \newcommand{\numNoisyOfficeUNetEpochs}{\emph{426}}
@@
 
-The \emph{Augraphy} library is designed to produce training datasets, pairing synthetic dirty documents with their clean ground truth document image sources.
-The need for such a data augmentation tool in document image analysis primarily results from the lack of ground truth images being available for most of the documents recorded within human history.
-Access to the knowledge stored in such document images is thwarted by artifacts, distortion and noise.
-As such, there is an ongoing need to improve available techniques to restore document images and thereby unlocking their contents for use in search or other document analysis tasks.
+The \emph{Augraphy} library is designed to introduce realistic degradations to images of documents, producing training datasets for supervised learning by pairing synthetic dirty documents with their clean ground truth document image sources.
+The need for such a data augmentation tool in document image analysis is twofold: existing document analytics software must be robust against various forms of noise, and ground truth images are unavailable for most of the documents recorded within human history.
+Automated recovery of knowledge stored in such documents is thwarted by the presence of distortion artifacts, which typically increase with time.
+As such, there is an ongoing \textit{and growing} need to improve both document restoration techniques and software processes, unlocking contents for use in search or other tasks and providing challenging data for tooling development.
+Augraphy answers this demand by supporting document-modality tasks such as reconstruction (Figure~\ref{fig:intro}), denoising (Figure~\ref{fig:shabbypages_denoising}), and robustness testing (Figure~\ref{fig:ocr_output}).
 
@@
 
-Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and daily life.
-Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, degraded text where low ink, annotations, highlighters or other markings add noise to the page that perturb semantic access by digital means.
+Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and regular use.
+Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, and degraded text where low ink, annotations, highlighters, or other markings add noise that hinder semantic access by digital means.
 
@@
                 \includegraphics{figures/archetype-memo.pdf}}}      \\
-        %(a) & (b) & (c) \\
     \end{tabularx}
 
-    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP.
-We demonstrate this by creating a noisy reproduction via \emph{Augraphy} augmentations against a clean reproduction.}
+    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, a real-life sample from RVL-CDIP.
+We demonstrate this by reproducing a clean image, then introducing noise with \emph{Augraphy}.}
 
@@
 Several research efforts have used \emph{Augraphy}: Larson et al.
-(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al.
-2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
+(2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al (2022) \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al.
+(2022) \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
 
@@
 
-Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools.
-This analysis highlights that most existing data augmentation libraries do not specifically cater to the corruptions typically encountered in document image analysis datasets.
-In contrast, \emph{Augraphy} is designed to be easily integrated into machine learning pipelines alongside popular Python packages used in machine learning and document analysis.
-Our paper also utilizes robustness testing to demonstrate how \emph{Augraphy} can be used to evaluate a model's effectiveness in the face of challenging conditions.
-Instead of general image modifications, we focus on document-specific distortions and alterations that are better suited to challenge OCR models with document images that still retain sufficient quality to remain human-readable.
+Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools, highlighting that most existing data augmentation libraries do not specifically cater to the corruptions typically encountered in document image analysis datasets.
+Instead of general image manipulation, \emph{Augraphy} focuses on document-specific distortions and alterations that are better-suited to challenging and evaluating OCR, object-detection, and other models with images which still retain sufficient quality to remain human-readable.
+Crucially, \emph{Augraphy} is also designed to be easily integrated into machine learning pipelines alongside other popular Python packages used in machine learning and document analysis.
 
@@
 In contrast, as seen in Table~\ref{tab:augmentation-library-comparison}, only \emph{Augraphy} offers a data augmentation library that supports imitating the corruptions commonly seen in document analysis corpora and is also easily integrated in modern machine learning training processes which rely on Python, including use of specialized paper, ink and post-processing pipelines not seen elsewhere.
-In fact, we attempted to recreate the document in Figure~\ref{fig:intro} using \emph{Albumentations} in preparation for presenting such a comparison in this paper, but the results were so poor and unlike the target we aimed to reproduce that we felt our effort would not have been taken seriously.
+Best-effort attempts to use \emph{Albumentations} to recreate the document in Figure~\ref{fig:intro} yielded results so poor and unlike the target that we could not in good faith include them in this paper.
 
-\emph{DocCreator}~\cite{ref_DocCreator} is the next best option, which provides an image-synthesizing tool for creating synthetic images that mimic common corruptions seen in document collections.
+\emph{DocCreator} \cite{ref_DocCreator} is the next best option, providing an image-synthesizing tool for creating synthetic images that mimic common corruptions seen in document collections.
 However, \emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
@@
 \emph{DocCreator} was also written in the C++ programming language as a monolithic \emph{what-you-see-is-what-you-get (WYSIWYG)} tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
-\emph{Augraphy}, on the other hand, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch~\cite{ref_pytorch}.
+\emph{Augraphy}, on the other hand, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_pytorch}.
 
@@
 
-Prior work for evaluating image classification and object detection models includes image blur; contrast, brightness and color alterations; masking; geometric transforms; pixel-level noise; and JPEG compression artefacts (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
+Prior work for evaluating image classification and object detection models includes image blur; contrast, brightness and color alterations; masking; geometric transforms; pixel-level noise; and compression artefacts (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
 More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
-Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, using specialized document-centric alterations to produce human-readable distortions which challenge OCR and face-detection models.
+Our paper also uses robustness testing of OCR and face-detection models, as a way to showcase \emph{Augraphy's} efficacy in producing document-centric distortions which challenge these models while remaining human-readable.
 
@@
 DocCreator's 3D mesh support here is excellent and has inspired \emph{Augraphy} to add similar functionality in its roadmap.
-In the meantime, \emph{Augraphy} currently offers support for paper folds.
+In the meantime, \emph{Augraphy} currently offers support for paper folds and book bindings.
 \end{enumerate}
-
-\begin{figure}
-\centering
-\scalebox{0.3}{
-\includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
-\label{fig:pipeline}
-\end{figure}
-
-\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
-The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".
-
-The paper phase applies transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
-After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-
-After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
-Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
 
@@
 
-\emph{Augraphy} is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
-The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
+\emph{Augraphy} is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so care was taken to establish good defaults.
+\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
+The default \emph{Augraphy} pipeline (used in the code snippet above) makes use of all of these augmentations, with starting parameters selected after manual visual inspection of thousands of images.
+Users of the library can define directed acyclic graphs of image transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
 
-\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
-Users of the library can define directed acyclic graphs of images and their transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
+\begin{figure}
+\centering
+\scalebox{0.3}{
+\includegraphics[]{figures/pipeline.png}}
+\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
+\label{fig:pipeline}
+\end{figure}
+
+\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
+The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically-faulty printer, or fading over time --- and transform them prior to ``printing".
+
+The paper phase applies transformations to the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
+After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
+
+After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
+Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
+Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
 
@@
     \centering
-    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within the pipeline.
+    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within a pipeline.
 Augmentations that work well in more than one phase are listed in the last column.}
@@
         & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
-        & & \textsf{Markup} & \textsf{NoiseTexturize}\\
-        & & \textsf{Faxify} & \textsf{PencilScribbles}\\
-        & & \textsf{PageBorder} & \\
+        & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
+        & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
+        & \textsf{PatternGenerator}& \textsf{PageBorder} & \\
+        & & & \\
         \bottomrule
@@
 
-Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} also includes these types of augmentations for completeness and utility.
+In addition to document-specific transformations, \emph{Augraphy} also includes transformations like blur, scaling, and rotation, reducing the need for additional general-purpose augmentation libraries.
 Descriptions of all \emph{Augraphy} augmentations are available online, along with the motivation for their development and usage examples. \footnote{\url{https://augraphy.readthedocs.io/en/latest/}}
@@
 \subsection{The Library}
-There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality that when composed generate realistic synthetically-augmented document images:
+There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality, and when composed generate realistic synthetically-augmented document images:
 
@@
 \noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
-In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
+In practice, these are model the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
 
@@
 
-Consider the following sequence of events:
+Consider the following sequence:
 \begin{quote}
   \begin{enumerate}
-  \item Ink is adhered to the paper material during the initial printing of a document.
+  \item Ink is adhered to paper material during the initial printing of a document.
   \item The document is attached to a public bulletin board in a high-traffic area.
-  \item Over a period of several weeks, it is annotated, defaced, and eventually torn away from its securing staples, flying away in the wind.
-  \item Fifty years later, our protagonist page is discovered by cleaning staff, who turn it over to library archivists.
-  \item These conservationists use delicate tools to gently position and record an image of the document, storing this in a digital repository.
+  \item The pages are annotated, defaced, and eventually torn away from their securing staples, flying away in the wind.
+  \item Fifty years later, the tattered pages are discovered and turned over to library archivists.
+  \item These conservationists use delicate tools to carefully position and record images of the document, storing these in a digital repository.
   \end{enumerate}
 \end{quote}
-An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.
+An \texttt{AugmentationPipeline} represents such document lifetimes by composing augmentations modeling each of these individual events, while collecting runtime metadata about augmentations and their parameters and storing copies of intermediate images, allowing for inspection and fine-tuning to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.
 
@@
 Effectively capturing processes like these in reproducible augmentations means separating our model of a document pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
-Producing realistically noisy document images can now be reduced to the definition and application of one or more \emph{Augraphy} pipelines to some clean, born-digital document images.
+With \emph{Augraphy}, producing realistically-noisy document images can be reduced to the definition and application of one or more \emph{Augraphy} pipelines to some clean, born-digital document images.
 
@@
 We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%.
-This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data that remains human readable suitable for evaluating OCR systems.
+This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data that remains human-readable, suitable for evaluating OCR systems.
 
@@
 \centering
-\includegraphics[width=0.9\columnwidth, frame]{figures/ocr_figure.png}
+\includegraphics[width=0.9\columnwidth]{figures/ocr_figure.png}
 \caption{Sample \emph{ShabbyReal} clean/noisy image pair, and the OCR output for each. The computed Levenshtein distance between the OCR result strings is 203.}
@@
         Azure & 57.1\%\\
-        Google & 60.1\%  \\
-        Amazon & 49.1\% \\
+        Google & 60.1\%\\
+        Amazon & 49.1\%\\
         UltraFace & 4.5\%\\
@@
 \end{wraptable}
-In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
-Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
-In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
-Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.
+In this section, we move beyond text-related tasks to robustness analysis of image classifiers and object detectors.
+In particular, we examine the robustness of face detection models on \emph{Augraphy}-altered images containing faces, such as newspapers \cite{newspaper-navigator} and legal identification documents \cite{midv-500}, which are often captured with noisy scanners.
 
-We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}.
-Then, we use \emph{Augraphy} to generate 10 altered versions of each image and manually remove any augmented image where the face(s) is not reasonably visible.
+We begin by sampling 75 images from the FDDB face detection benchmark \cite{fddbTech}, using \emph{Augraphy} to generate 10 altered versions of each image, manually removing any augmented image where the face(s) is not reasonably visible.
 We then test four face detection models on the noisy and noise-free images.
 These models are: proprietary face detection models from Google,\footnote{\url{https://cloud.google.com/vision/docs/detecting-faces}} Amazon,\footnote{\url{https://aws.amazon.com/rekognition/}} and Microsoft\footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services/face}}, and lastly the freely-available UltraFace\footnote{\url{https://github.com/onnx/models/tree/main/vision/body_analysis/ultraface}} model.
-%We then test Microsoft Azure's face detection model on the noise-free and noisy images.
 

### 2023-04-29 paper.tex
revert to previous format, update augmentations table

@@
 
-Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and regular use.
-Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, and degraded text where low ink, annotations, highlighters, or other markings add noise that hinder semantic access by digital means.
-
 \begin{figure}
@@
 \end{figure}
+
+Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and regular use.
+Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, and degraded text where low ink, annotations, highlighters, or other markings add noise that hinder semantic access by digital means.
 
@@
 
+\begin{figure}
+\centering
+\scalebox{0.3}{
+\includegraphics[]{figures/pipeline.png}}
+\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
+\label{fig:pipeline}
+\end{figure}
+
+\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
+The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically-faulty printer, or fading over time --- and transform them prior to ``printing".
+
+The paper phase applies transformations to the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
+After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
+
+After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
+Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
+Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
+
 \section{Augraphy}
@@
 Users of the library can define directed acyclic graphs of image transformations via the \texttt{AugraphyPipeline} API, representing the passage of a document through real-world alterations.
-
-\begin{figure}
-\centering
-\scalebox{0.3}{
-\includegraphics[]{figures/pipeline.png}}
-\caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
-\label{fig:pipeline}
-\end{figure}
-
-\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into \emph{three phases}: \textbf{ink}, \textbf{paper}, and \textbf{post}.
-The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically-faulty printer, or fading over time --- and transform them prior to ``printing".
-
-The paper phase applies transformations to the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator creates a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
-After the ink and paper textures are separately computed, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
-
-After ``printing", the document enters the post phase, wherein it may undergo modifications that might alter an already-printed document out in the world.
-Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or color highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
-Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.
 
@@
         \textsf{BleedThrough} & \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
-        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
-        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
-        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
-        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
+        \textsf{LowInkPeriodicLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
+        \textsf{LowInkRandomLines} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
+        \textsf{InkBleed} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
+        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
         & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
         & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
-        & \textsf{PatternGenerator}& \textsf{PageBorder} & \\
-        & & & \\
+        & \textsf{PatternGenerator}& \textsf{PageBorder} & \textsf{LinesDegradation}\\
+        & & & \textsf{Brightness}\\
         \bottomrule

### 2023-04-30 paper.tex
Minor edits

@@
         \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
-        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
+        \textbf{\emph{Augraphy} (ours)} & \textbf{\numAugraphyAugmentations} & \cmark & \cmark & \cmark & \textbf{MIT}\\
     \bottomrule
@@
 
-Some techniques exist for introducing these features into images of documents, including but not limited to the following:
+\begin{samepage}
+\noindent Some techniques exist for introducing these features into images of documents, including but not limited to the following:
 \begin{enumerate}
-\item Text can be generated independently of the paper texture, and can be overlaid onto the ``paper'' by a number of blending functions, allowing a variety of paper textures to be used.
+\item Text can be generated independently of the paper texture, overlaid onto the ``paper'' by a number of blending functions, allowing use of a variety of paper textures.
 \item Similarly, any markup features may be generated and overlaid by the same methods.
@@
 \end{enumerate}
+\end{samepage}
 
@@
 \noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
-In practice, these are model the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
+In practice, these model the pipeline phases discussed previously with lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
 

### 2023-04-30 paper.tex
Fixed a few latex errors

@@
 \usepackage[colorlinks]{hyperref}
-\hypersetup{
-    colorlinks = false,
-    linkbordercolor = {blue}
-}
 \usepackage{listings}
+\usepackage{enumitem}
 \usepackage{courier}
@@
 \newcommand{\xmark}{{\color{Maroon}\ding{55}}}%
+
+\hypersetup{
+    colorlinks = false,
+    linkbordercolor = {blue}
+}
 
@@
 
-\begin{table}[]
+\begin{table}
     \centering
@@
 \scalebox{0.3}{
-\includegraphics[]{figures/pipeline.png}}
+\includegraphics{figures/pipeline.png}}
 \caption{Visualization of an \emph{Augraphy} pipeline, showing the composition of several image augmentations together with a specific paper background}
@@
 
-Consider the following sequence:
-\begin{quote}
-  \begin{enumerate}
+\smallskip
+\noindent~Consider the following sequence:
+\begin{enumerate}[leftmargin=4em]
   \item Ink is adhered to paper material during the initial printing of a document.
@@
 \end{enumerate}
-\end{quote}
+
 An \texttt{AugmentationPipeline} represents such document lifetimes by composing augmentations modeling each of these individual events, while collecting runtime metadata about augmentations and their parameters and storing copies of intermediate images, allowing for inspection and fine-tuning to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.

### 2023-04-30 paper.tex

@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
+\caption{Examples of some \emph{Augraphy} augmentations.} \label{fig2}
+\end{figure}
+
 \subsection{Augraphy Augmentations}
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/augmentation-matrix.png}
-\caption{Examples of some \emph{Augraphy} augmentations.} \label{fig2}
-\end{figure}
-
 \section{Deep Learning with \emph{Augraphy}}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/shabbyreal_denoised.png}
+\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
+\label{fig:shabbyreal_denoised}
+\end{figure}
+
 \subsection{Training Regime}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.95\columnwidth]{figures/shabbypages_denoising.png}
+\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
+\label{fig:shabbypages_denoising}
+\end{figure}
+
+\begin{samepage}
 \subsection{Results}
@@
 To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.
+\end{samepage}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/shabbyreal_denoised.png}
-\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
-\label{fig:shabbyreal_denoised}
-\end{figure}
-
 As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\columnwidth]{figures/shabbypages_denoising.png}
-\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
-\label{fig:shabbypages_denoising}
-\end{figure}
 
@@
 \section{Conclusion and Future Work}
-We presented \emph{Augraphy}, a framework for generating realistic synthetically-augmented datasets of document images.
-Other available image augmentation tools were examined and found to lack features needed for our purposes, motivating the creation of this library specifically targeting the types of alterations and degradations seen in document images.
+We presented \emph{Augraphy}, a framework licensed under the MIT open source license for generating realistic synthetically-augmented datasets of document images.
+Other available tools were examined and found to lack needed features, motivating the creation of this library specifically supporting alterations and degradations seen in document images.
 
-We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.
+We described how to use \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.
 
@@
 
-Future work on the \emph{Augraphy} library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on commodity hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions, and responding to community-initiated feature requests.
-
-\emph{Augraphy} is licensed under the MIT open source license, and readers are invited to share feedback and participate in its development on GitHub.
+Future work on the \emph{Augraphy} library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets, providing more scale-invariant support for all document image resolutions, and responding to community-initiated feature requests.
 

### 2023-04-30 paper.tex
Fixed over-hanging line that was too long for page width

@@
 \smallskip
-\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
-In practice, these model the pipeline phases discussed previously with lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.
+\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- intended to be applied in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
+In practice, these model the pipeline phases discussed previously with lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} applied in each \texttt{AugmentationPipeline} phase, and in each case yield the image, transformed by some of the Augmentations in the sequence.
 
